---
title: "MFCL outputs"
author: "kyuhan Kim"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: yes
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# =============================================================================
# SETUP BLOCK: Load packages, data, and define global configurations
# =============================================================================

knitr::opts_chunk$set(
  dev = "png",
  dpi = 160,
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = '../report/Figures/'
)

# -----------------------------------------------------------------------------
# 1. LOAD REQUIRED PACKAGES
# -----------------------------------------------------------------------------
library(ggplot2)
library(cowplot)
library(dplyr)
library(FLR4MFCL)
library(tidyr)
library(patchwork)
library(reshape2)
library(kableExtra)
library(viridis)
library(stringr)
library(purrr)

theme_set(theme_cowplot())
source("../tools/plot_utils.R")

# -----------------------------------------------------------------------------
# 2. CHUNK EVALUATION CONTROL
# Set TRUE/FALSE to enable/disable each section
# -----------------------------------------------------------------------------

RUN_CHUNKS <- list(
  model_summary      = TRUE,   # Model summary table
  bound_hit          = TRUE,   # Bound hit parameter analysis
  spawning_depletion = TRUE,   # SB/SBF0 and recruitment plots
  cpue_by_scenario   = TRUE    # CPUE fits by scenario
)

# -----------------------------------------------------------------------------
# 3. PATHS
# -----------------------------------------------------------------------------
MODEL_DIR <- file.path(getwd(), "..", "model")

# -----------------------------------------------------------------------------
# 4. FISHERY MAPPING FUNCTIONS
# These functions handle automatic fishery name assignment
# -----------------------------------------------------------------------------

#' Create fishery mapping from model data
#' @param par_obj MFCLPar object (to get number of fisheries)
#' @param custom_map Optional named vector of custom fishery names
#' @return Named vector with fishery numbers as names and names as values
create_fishery_map <- function(par_obj, custom_map = NULL) {
  n_fisheries <- par_obj@dimensions["fisheries"]
  
  # Default: "Fishery-1", "Fishery-2", etc.
  default_map <- setNames(
    paste0("Fishery-", 1:n_fisheries),
    as.character(1:n_fisheries)
  )
  
  # Override with custom names if provided
  if (!is.null(custom_map)) {
    for (i in names(custom_map)) {
      if (i %in% names(default_map)) {
        default_map[i] <- custom_map[i]
      }
    }
  }
  
  return(default_map)
}

#' Get fishery name with fallback
#' @param fishery_num Fishery number
#' @param mapping Named vector of fishery mappings
#' @return Character string with fishery name
get_fishery_name <- function(fishery_num, mapping = NULL) {
  if (is.null(mapping)) {
    return(paste0("Fishery-", fishery_num))
  }
  
  key <- as.character(fishery_num)
  name <- mapping[key]
  
  if (is.na(name) || is.null(name)) {
    return(paste0("Fishery-", fishery_num))
  } else {
    return(unname(name))
  }
}

#' Apply fishery names to vector
#' @param fishery_nums Vector of fishery numbers
#' @param mapping Named vector of fishery mappings
#' @return Character vector of fishery names
apply_fishery_names <- function(fishery_nums, mapping = NULL) {
  sapply(fishery_nums, function(x) get_fishery_name(x, mapping))
}

#' Detect index fisheries (ending with 'i' or containing 'index')
#' @param fishery_map Named vector of fishery mappings
#' @return Character vector of index fishery numbers
detect_index_fisheries <- function(fishery_map) {
  is_index <- grepl("i$|index", fishery_map, ignore.case = TRUE)
  names(fishery_map)[is_index]
}

# Plot aesthetics (named 'config' for compatibility with plot_utils.R functions)
config <- list(
  alpha = 0.7,
  linewidth = 1,
  point_size = 2.5,
  observed_color = "grey30",
  predicted_color = NULL,  # NULL means use viridis colors
  predicted_colors = NULL,
  legend_position = "bottom",
  facet_ncol = 3,
  show_title = TRUE,
  custom_title = NULL
)


# -----------------------------------------------------------------------------
# 5. HELPER FUNCTIONS
# -----------------------------------------------------------------------------

#' Safely read a file, returning NULL if it doesn't exist
safe_read <- function(path, reader = readLines) {
  if (file.exists(path)) reader(path) else NULL
}

#' Parse indepvar.rpt file
parse_indepvar <- function(lines) {
  if (is.null(lines) || length(lines) < 2) return(NULL)
  
  data_list <- lapply(2:length(lines), function(i) {
    line <- lines[i]
    if (nchar(trimws(line)) == 0) return(NULL)
    
    hit_bound <- grepl("\\*{5,}", line)
    line_clean <- gsub("\\*+", "", line)
    parts <- strsplit(trimws(line_clean), "\\s+")[[1]]  # Use [[1]] to extract the vector
    
    if (length(parts) >= 6) {
      data.frame(
        Index = as.integer(parts[1]),
        Var_name = parts[2],
        Estimate = as.numeric(parts[3]),
        L_bound = as.numeric(parts[4]),
        U_bound = as.numeric(parts[5]),
        Gradient = as.numeric(parts[6]),
        Hit_Bound = hit_bound,
        stringsAsFactors = FALSE
      )
    } else {
      NULL
    }
  })
  
  do.call(rbind, Filter(Negate(is.null), data_list))
}

#' Generate scenario color palette
get_scenario_colors <- function(scenarios, option = "D") {
  setNames(viridis(length(scenarios), option = option, direction = 1), scenarios)
}

# -----------------------------------------------------------------------------
# 6. CUSTOM FISHERY NAMES (OPTIONAL)
# Only define the fisheries you know - others will be auto-numbered
# -----------------------------------------------------------------------------

# Option 1: Scenario-specific names
SCENARIO_FISHERY_NAMES <- list(
  # Example:
  # "base" = c("1" = "LL-Region1", "2" = "LL-Region2"),
  # "retro_2020" = c("1" = "LL-Region1", "2" = "LL-Region2")
)

# Option 2: Global names (applied to all scenarios unless overridden)
GLOBAL_FISHERY_NAMES <- c(
  # Longline
  "1" = "LL-ALL-1", "2" = "LL-ALL-2", "3" = "LL-US-2", "4" = "LL-ALL-3",
  "5" = "LL-OS-3", "6" = "LL-OS-7", "7" = "LL-ALL-7", "8" = "LL-ALL-8",
  "9" = "LL-ALL-4", "10" = "LL-AU-5", "11" = "LL-ALL-5", "12" = "LL-ALL-6",
  "27" = "LL-AU-9", "29" = "LL-ALL-9",
  
  # Purse seine
  "13" = "PS-ASS-3", "14" = "PS-UNA-3", "15" = "PS-ASS-4", "16" = "PS-UNA-4",
  "19" = "PS-JP-1", "24" = "PS-PHID-7", "25" = "PS-ASS-8", "26" = "PS-UNA-8",
  "30" = "PS-ASS-7", "31" = "PS-UNA-7",
  
  # Pole and line
  "20" = "PL-JP-1", "21" = "PL-ALL-3", "22" = "PL-ALL-8", "28" = "PL-ALL-7",
  
  # Miscellaneous
  "17" = "MISC-PH-7", "18" = "HL-PHID-7", "23" = "MISC-ID-7", "32" = "MISC-VN-7",
  
  # Index fisheries
  "33" = "LL-ALL-1i", "34" = "LL-ALL-2i", "35" = "LL-ALL-3i",
  "36" = "LL-ALL-4i", "37" = "LL-ALL-5i", "38" = "LL-ALL-6i",
  "39" = "LL-ALL-7i", "40" = "LL-ALL-8i", "41" = "LL-ALL-9i"
)

# -----------------------------------------------------------------------------
# 7. LOAD MODEL DATA
# -----------------------------------------------------------------------------

# Get all model folders
model_folders <- list.dirs(MODEL_DIR, full.names = TRUE, recursive = FALSE)
model_names <- basename(model_folders)

# Load data from each model folder
results <- setNames(lapply(model_folders, function(folder) {
  cat("Processing folder:", basename(folder), "\n")
  
  # Read core model outputs
  par_out <- read.MFCLPar(finalPar(folder))
  rep_out <- read.MFCLRep(finalRep(folder))
  
  # Read optional files
  indep_out <- safe_read(file.path(folder, "indepvar.rpt"))
  
  # Check if model_info.rds exists
  info_file <- file.path(folder, "model_info.rds")
  info <- if (file.exists(info_file)) readRDS(info_file) else list()
  
  list(
    ParOut = par_out,
    RepOut = rep_out,
    IndepOut = indep_out,
    info = info
  )
}), model_names)

# -----------------------------------------------------------------------------
# 8. CREATE SCENARIO-SPECIFIC FISHERY MAPPINGS
# -----------------------------------------------------------------------------

# Create fishery mapping for each scenario
FISHERY_MAPS <- lapply(names(results), function(scenario_name) {
  par_obj <- results[[scenario_name]]$ParOut
  
  # Check if scenario has custom names
  custom_names <- if (scenario_name %in% names(SCENARIO_FISHERY_NAMES)) {
    SCENARIO_FISHERY_NAMES[[scenario_name]]
  } else {
    GLOBAL_FISHERY_NAMES  # Use global names as fallback
  }
  
  # Create mapping
  create_fishery_map(par_obj, custom_names)
})
names(FISHERY_MAPS) <- model_names

# Create index fishery lists for each scenario
INDEX_FISHERIES_MAPS <- lapply(FISHERY_MAPS, detect_index_fisheries)

# Print summary
cat("\n=== Fishery Mapping Summary ===\n")
for (scenario in names(FISHERY_MAPS)) {
  n_fish <- length(FISHERY_MAPS[[scenario]])
  n_index <- length(INDEX_FISHERIES_MAPS[[scenario]])
  cat(sprintf("%s: %d fisheries (%d index)\n", scenario, n_fish, n_index))
}

# -----------------------------------------------------------------------------
# 9. EXTRACT DATA INTO NAMED LISTS
# -----------------------------------------------------------------------------

ParOut_list <- map(results, "ParOut")
RepOut_list <- map(results, "RepOut")
IndepOut_list <- map(results, "IndepOut")
Info_list <- map(results, "info")

# Extract year range for each model
YearRanges <- map(ParOut_list, function(par) {
  list(
    minYear = par@range["minyear"],
    maxYear = par@range["maxyear"]
  )
})

# Print summary
cat("\n=== Year Range Summary ===\n")
for (scenario in names(YearRanges)) {
  cat(sprintf("%s: %d - %d\n", 
              scenario, 
              YearRanges[[scenario]]$minYear, 
              YearRanges[[scenario]]$maxYear))
}

```

# Summary of each model configuration

```{r model-summary, echo=FALSE, message=FALSE, fig.dim=c(10,10), eval=RUN_CHUNKS$model_summary}
# =============================================================================
# MODEL SUMMARY TABLE
# Extracts key parameters from each model for comparison
# =============================================================================

# Extract parameters from each model
params_df <- imap_dfr(ParOut_list, function(par, model_name) {
  
  # Safely extract values with error handling
  get_slot <- function(slot_name, default = NA) {
    tryCatch(slot(par, slot_name), error = function(e) default)
  }
  
  dims <- tryCatch(
    as.list(par@dimensions),
    error = function(e) list(
      agecls = NA, years = NA, seasons = NA,
      regions = NA, fisheries = NA, taggrps = NA
    )
  )
  
  data.frame(
    Model = model_name,
    mgc = round(as.numeric(get_slot("max_grad")), 6),
    obj_fun = round(as.numeric(get_slot("obj_fun")), 2),
    n_pars = as.numeric(get_slot("n_pars")),
    agecls = dims$agecls,
    years = dims$years,
    seasons = dims$seasons,
    regions = dims$regions,
    fisheries = dims$fisheries,
    taggrps = dims$taggrps
  )
})

# Display table
kable(params_df, caption = "Basic model info") %>%
  kable_styling(full_width = FALSE)
```


# Bound Hit Parameter Analysis {.tabset .tabset-pills}

```{r bound-hit-analysis, echo=FALSE, message=FALSE, warning=FALSE, results='asis', eval=RUN_CHUNKS$bound_hit}
# =============================================================================
# BOUND HIT ANALYSIS
# Identifies parameters that hit their bounds during optimization
# =============================================================================

# Separate models with and without indepvar.rpt
null_models <- names(IndepOut_list)[sapply(IndepOut_list, is.null)]
valid_models <- names(IndepOut_list)[!sapply(IndepOut_list, is.null)]

# Process each valid model
model_results <- map(setNames(valid_models, valid_models), function(model_name) {
  
  df <- parse_indepvar(IndepOut_list[[model_name]])
  if (is.null(df)) return(NULL)
  
  # Calculate distances to bounds
  df <- df %>%
    mutate(
      Distance_to_lower = abs(Estimate - L_bound),
      Distance_to_upper = abs(Estimate - U_bound),
      Hit_Type = case_when(
        !Hit_Bound ~ "None",
        Distance_to_lower <= Distance_to_upper ~ "Lower",
        TRUE ~ "Upper"
      ),
      Distance_to_bound = if_else(
        Hit_Bound,
        if_else(Hit_Type == "Lower", Distance_to_lower, Distance_to_upper),
        NA_real_
      ),
      Var_type = str_extract(Var_name, "^[a-zA-Z_]+")
    )
  
  # Extract bound hits
  bound_hits <- df %>%
    filter(Hit_Bound) %>%
    select(Index, Var_name, Var_type, Estimate, Hit_Type,
           L_bound, U_bound, Distance_to_bound, Gradient) %>%
    arrange(Index)
  
  # Save to CSV
  write.csv(bound_hits, paste0("bound_hits_", model_name, ".csv"), row.names = FALSE)
  
  list(total_params = nrow(df), bound_hits = bound_hits)
})

# Remove NULL results
model_results <- Filter(Negate(is.null), model_results)

# --- Overview Tab ---
cat("\n## Overview\n\n")

cat(sprintf("**Total Models:** %d  \n", length(IndepOut_list)))
cat(sprintf("**Models with indepvar.rpt:** %d  \n", length(valid_models)))
cat(sprintf("**Models without indepvar.rpt:** %d  \n\n", length(null_models)))

if (length(model_results) > 0) {
  overview <- data.frame(
    Model = names(model_results),
    Total_Params = sapply(model_results, function(x) x$total_params),
    Bound_Hits = sapply(model_results, function(x) nrow(x$bound_hits)),
    Hit_Rate = sapply(model_results, function(x) 
      sprintf("%.2f%%", nrow(x$bound_hits) / x$total_params * 100)),
    Lower_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Lower")),
    Upper_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Upper"))
  )
  
  print(
    kable(overview,
          col.names = c("Model", "Total", "Hits", "Rate", "Lower", "Upper"),
          align = c("l", "r", "r", "r", "r", "r"),
          row.names = FALSE) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE) %>%
      row_spec(0, bold = TRUE, background = "#2196F3", color = "white") %>%
      column_spec(3, bold = TRUE, color = "red")
  )
}

# List models without indepvar.rpt
if (length(null_models) > 0) {
  cat("\n\n### Models Without indepvar.rpt\n\n")
  cat("The following models did not generate an `indepvar.rpt` file:\n\n")
  for (model in null_models) {
    cat(sprintf("- **%s**: `indepvar.rpt` was not generated\n", model))
  }
  cat("\n")
}

# --- Individual Model Tabs ---
for (model_name in names(model_results)) {
  result <- model_results[[model_name]]
  bound_hits <- result$bound_hits
  
  cat(sprintf("\n## %s\n\n", model_name))
  
  cat(sprintf("**Total Parameters:** %s  \n", format(result$total_params, big.mark = ",")))
  cat(sprintf("**Bound Hits:** %d (%.2f%%)  \n", 
              nrow(bound_hits), nrow(bound_hits) / result$total_params * 100))
  cat(sprintf("**Lower Bound Hits:** %d  \n", sum(bound_hits$Hit_Type == "Lower")))
  cat(sprintf("**Upper Bound Hits:** %d  \n\n", sum(bound_hits$Hit_Type == "Upper")))
  
  if (nrow(bound_hits) > 0) {
    cat("### Bound Hit Parameters\n\n")
    
    bound_hits_display <- bound_hits %>%
      mutate(
        Estimate_fmt = sprintf("%.4e", Estimate),
        Distance_fmt = sprintf("%.2e", Distance_to_bound)
      ) %>%
      select(Index, Var_name, Var_type, Estimate_fmt, Hit_Type, 
             L_bound, U_bound, Distance_fmt)
    
    print(
      kable(bound_hits_display,
            col.names = c("Index", "Parameter", "Type", "Estimate", "Hit",
                          "Lower", "Upper", "Distance"),
            align = c("r", "l", "l", "r", "c", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                      full_width = TRUE, font_size = 11) %>%
        row_spec(0, bold = TRUE, background = "#4CAF50", color = "white") %>%
        column_spec(5, bold = TRUE,
                    color = ifelse(bound_hits$Hit_Type == "Lower", "#E74C3C", "#3498DB")) %>%
        scroll_box(width = "100%", height = "400px")
    )
    
    cat("\n\n### Summary by Variable Type\n\n")
    
    type_summary <- bound_hits %>%
      count(Var_type, Hit_Type) %>%
      pivot_wider(names_from = Hit_Type, values_from = n, values_fill = 0) %>%
      mutate(Total = Lower + Upper) %>%
      arrange(desc(Total))
    
    print(
      kable(type_summary,
            col.names = c("Type", "Lower", "Upper", "Total"),
            align = c("l", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover"),
                      full_width = FALSE) %>%
        row_spec(0, bold = TRUE, background = "#FF9800", color = "white") %>%
        column_spec(4, bold = TRUE)
    )
    
    cat(sprintf("\n\n*Data saved to: `bound_hits_%s.csv`*\n\n", model_name))
  } else {
    cat("\n✅ **No bound hits detected in this model**\n\n")
  }
}

# --- NULL Model Tabs ---
for (model_name in null_models) {
  cat(sprintf("\n## %s\n\n", model_name))
  cat("⚠️ **No `indepvar.rpt` file.**\n\n")
}
```


# Spawning Depletion

```{r spawning-depletion, echo=FALSE, message=FALSE, fig.dim=c(8,6), eval=RUN_CHUNKS$spawning_depletion}
# =============================================================================
# SPAWNING BIOMASS DEPLETION AND RECRUITMENT
# =============================================================================

# Get global min/max years across all scenarios
all_min <- min(sapply(YearRanges, function(x) x$minYear))
all_max <- max(sapply(YearRanges, function(x) x$maxYear))

# Extract spawning biomass depletion using GetQuantSimple approach
SBdep <- map_dfr(names(RepOut_list), function(scenario) {
  rep_obj <- RepOut_list[[scenario]]
  minYear <- YearRanges[[scenario]]$minYear
  maxYear <- YearRanges[[scenario]]$maxYear
  
  # Get all values
  sb_all <- SBSBF0(rep_obj)
  
  # Get actual years from the data
  actual_years <- as.numeric(names(sb_all))
  
  # If no names, use sequential years
  if (length(actual_years) == 0 || all(is.na(actual_years))) {
    actual_years <- minYear:(minYear + length(sb_all) - 1)
  }
  
  # Filter to scenario's year range
  year_filter <- actual_years >= minYear & actual_years <= maxYear
  
  data.frame(
    Scenario = scenario,
    Year = actual_years[year_filter],
    Quant = as.numeric(sb_all)[year_filter],
    stringsAsFactors = FALSE
  )
})

# Extract recruitment using GetQuantSimple approach
Rec <- map_dfr(names(RepOut_list), function(scenario) {
  rep_obj <- RepOut_list[[scenario]]
  minYear <- YearRanges[[scenario]]$minYear
  maxYear <- YearRanges[[scenario]]$maxYear
  
  # Get all values
  rec_all <- eq_rec(rep_obj)
  
  # Get actual years from the data
  actual_years <- as.numeric(names(rec_all))
  
  # If no names, use sequential years
  if (length(actual_years) == 0 || all(is.na(actual_years))) {
    actual_years <- minYear:(minYear + length(rec_all) - 1)
  }
  
  # Filter to scenario's year range
  year_filter <- actual_years >= minYear & actual_years <= maxYear
  
  data.frame(
    Scenario = scenario,
    Year = actual_years[year_filter],
    Quant = as.numeric(rec_all)[year_filter] / 1e6,
    stringsAsFactors = FALSE
  )
})

# Check data
cat("SBdep rows:", nrow(SBdep), "Scenarios:", paste(unique(SBdep$Scenario), collapse=", "), "\n")
cat("Rec rows:", nrow(Rec), "\n")

# Remove NA rows
SBdep <- SBdep[!is.na(SBdep$Quant), ]
Rec <- Rec[!is.na(Rec$Quant), ]

# Define color palette
scenario_levels <- unique(SBdep$Scenario)
scenario_colors <- get_scenario_colors(scenario_levels)

# Convert to factor
SBdep$Scenario <- factor(SBdep$Scenario, levels = scenario_levels)
Rec$Scenario <- factor(Rec$Scenario, levels = scenario_levels)

# Common theme
common_theme <- theme_bw() + theme(legend.position = "none")

# Plot 1: SB/SBF=0
SBdepPlot <- ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) +
  geom_line(linewidth = 1.2) +
  scale_color_manual(values = scenario_colors) +
  labs(x = "Year", y = bquote(SB/SB["F=0"])) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "darkred") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgreen") +
  common_theme

# Plot 2: Recruitment  
RecPlot <- ggplot(Rec, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) +
  geom_line(linewidth = 1.2) +
  coord_cartesian(ylim = c(0, NA)) +
  scale_color_manual(values = scenario_colors) +
  labs(x = "Year", y = bquote("Recruitment (" * 10^6 * ")")) +
  common_theme

# Extract legend
legend <- cowplot::get_legend(
  ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario)) +
    geom_line(linewidth = 2) +
    scale_color_manual(values = scenario_colors) +
    theme_bw() +
    theme(
      legend.position = "right",
      legend.title = element_text(face = "bold"),
      legend.key.width = unit(1.5, "cm")
    ) +
    labs(color = "Scenario")
)

# Combine plots
combined_plot <- cowplot::plot_grid(
  SBdepPlot, RecPlot,
  ncol = 1, labels = c("A", "B"), label_size = 12, align = "v"
)

final_plot <- cowplot::plot_grid(
  combined_plot, legend,
  ncol = 2, rel_widths = c(4, 1)
)

print(final_plot)


```


# CPUE plots {.tabset}

## Observed vs Fitted CPUE by scenario {.tabset .tabset-pills}

```{r cpue-by-scenario, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.dim=c(8,8), eval=RUN_CHUNKS$cpue_by_scenario}
# =============================================================================
# CPUE FITS BY SCENARIO
# Uses cpue_obs/cpue_pred from FLR4MFCL
# =============================================================================

for (scenario_name in names(RepOut_list)) {
  cat(sprintf("\n## %s\n\n", scenario_name))
  
  rep_obj <- RepOut_list[[scenario_name]]
  fishery_map <- FISHERY_MAPS[[scenario_name]]
  index_fisheries_nums <- INDEX_FISHERIES_MAPS[[scenario_name]]
  
  if (length(index_fisheries_nums) == 0) {
    cat("*No index fisheries detected for this scenario*\n\n")
    next
  }
  
  # Extract observed and predicted CPUE using FLR4MFCL functions
  tryCatch({
    obs <- as.data.frame(cpue_obs(rep_obj))
    fit <- as.data.frame(cpue_pred(rep_obj))
    
    # Standardize column names
    names(obs)[names(obs) == "data"] <- "obs"
    names(fit)[names(fit) == "data"] <- "fit"
    
    # Join data
    cpue <- merge(obs, fit)
    cpue <- type.convert(cpue, as.is = TRUE)
    
    # Filter to index fisheries only
    cpue <- cpue[cpue$unit %in% as.numeric(index_fisheries_nums), , drop = FALSE]
    
    if (nrow(cpue) == 0) {
      cat("*No CPUE data available for index fisheries*\n\n")
      next
    }
    
    # Apply fishery name mapping
    cpue$unit <- as.character(cpue$unit)
    cpue$fishery_name <- sapply(cpue$unit, function(x) get_fishery_name(x, fishery_map))
    
    # Transform data (assuming log-scale)
    cpue <- cpue %>%
      mutate(
        year_season = year + (season - 1) / 4,
        obs = exp(obs),
        fit = exp(fit)
      )
    
    # Create plot
    p <- ggplot(cpue, aes(x = year_season)) +
      geom_point(aes(y = obs, color = "Observed"), 
                 size = 2.5, alpha = 0.7, shape = 16) +
      geom_line(aes(y = fit, color = "Predicted"), 
                alpha = 0.8, linewidth = 1.2) +
      facet_wrap(~fishery_name, scales = "free_y", ncol = 3) +
      scale_color_manual(
        name = "",
        values = c("Observed" = "#E69F00", "Predicted" = "#56B4E9")
      ) +
      labs(
        title = paste(scenario_name, "- CPUE Fits"),
        x = "Year + Season",
        y = "CPUE"
      ) +
      theme_bw() +
      theme(
        legend.position = "top",
        strip.text = element_text(size = 10, face = "bold"),
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold")
      )
    
    print(p)
    
  }, error = function(e) {
    cat("*Error extracting CPUE data:*", conditionMessage(e), "\n\n")
  })
  
  cat("\n\n")
}
```


# LF plots {.tabset}

## Overlay all scenarios {.tabset .tabset-pills}

```{r lf-overlay, echo=FALSE, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis', eval=RUN_CHUNKS$lf_overlay}
# =============================================================================
# LENGTH FREQUENCY FITS - ALL SCENARIOS OVERLAID
# =============================================================================

# Get all unique fisheries across all scenarios
all_fisheries <- unique(unlist(lapply(LengOut_list, function(x) unique(x@lenfits$fishery))))

for (fish in all_fisheries) {
  # Get fishery name from first scenario that has this fishery
  fishery_name <- NULL
  for (sc in names(LengOut_list)) {
    if (fish %in% unique(LengOut_list[[sc]]@lenfits$fishery)) {
      fishery_map <- FISHERY_MAPS[[sc]]
      fishery_name <- get_fishery_name(fish, fishery_map)
      break
    }
  }
  
  if (is.null(fishery_name)) {
    fishery_name <- paste("Fishery", fish)
  }
  
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  # Combine data from all scenarios
  combined_data <- map_dfr(names(LengOut_list), function(sc) {
    df <- LengOut_list[[sc]]@lenfits
    if (fish %in% unique(df$fishery)) {
      df %>% 
        filter(fishery == fish) %>% 
        mutate(Scenario = sc)
    } else {
      NULL
    }
  })
  
  if (is.null(combined_data) || nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  # Aggregate by scenario, year, length (THIS IS KEY - ensure no duplicates)
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, length) %>%
    summarise(obs = sum(obs, na.rm = TRUE), 
              pred = sum(pred, na.rm = TRUE), 
              .groups = "drop") %>%
    filter(obs > 0 | pred > 0)  # Remove zero rows
  
  # Separate observed data (same across scenarios)
  obs_data <- plot_data %>%
    group_by(year, length) %>%
    summarise(obs = first(obs), .groups = "drop")  # Take first occurrence
  
  # Create plot
  p <- ggplot() +
    geom_col(data = obs_data, 
             aes(x = length, y = obs, fill = "Observed"), 
             alpha = 0.7, width = 2, position = "identity") +  # Added position
    geom_line(data = plot_data,
              aes(x = length, y = pred, color = Scenario), 
              linewidth = 1.2) +
    facet_wrap(~year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(
      title = paste(fishery_name, "- Length Frequency Fits"),
      x = "Length (cm)", 
      y = "Frequency"
    ) +
    theme_bw() +
    theme(
      legend.position = "top", 
      legend.box = "vertical",
      strip.text = element_text(size = 8),
      strip.background = element_rect(fill = "grey90"),
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5)
    )
  
  print(p)
  cat("\n\n")
}


```

## By scenario {.tabset .tabset-pills}

```{r lf-by-scenario, echo=FALSE, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis', eval=RUN_CHUNKS$lf_by_scenario}
# =============================================================================
# LENGTH FREQUENCY FITS BY SCENARIO
# =============================================================================

for (scenario_name in names(LengOut_list)) {
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- LengOut_list[[scenario_name]]
  fishery_map <- FISHERY_MAPS[[scenario_name]]
  
  # Get fisheries that exist in this scenario
  scenario_fisheries <- unique(scenario_data@lenfits$fishery)
  
  if (length(scenario_fisheries) == 0) {
    cat("*No length frequency data in this scenario*\n\n")
    next
  }
  
  for (fish in scenario_fisheries) {
    fishery_name <- get_fishery_name(fish, fishery_map)
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    # Extract and aggregate data for this fishery
    plot_data <- scenario_data@lenfits %>%
      filter(fishery == fish) %>%
      group_by(fishery, year, length) %>%
      summarise(obs = sum(obs, na.rm = TRUE), 
                pred = sum(pred, na.rm = TRUE), 
                .groups = "drop") %>%
      filter(obs > 0 | pred > 0)  # Remove zero rows
    
    if (nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    # Create plot
    p <- ggplot(plot_data, aes(x = length)) +
      geom_col(aes(y = obs, fill = "Observed"), 
               alpha = 0.7, width = 2, position = "identity") +  # Added position
      geom_line(aes(y = pred, color = "Predicted"), linewidth = 1.2) +
      facet_wrap(~year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(
        title = paste(scenario_name, "-", fishery_name, "- Length Frequency Fits"),
        x = "Length (cm)", 
        y = "Frequency"
      ) +
      theme_bw() +
      theme(
        legend.position = "top", 
        legend.box = "horizontal",
        strip.text = element_text(size = 8),
        strip.background = element_rect(fill = "grey90"),
        plot.title = element_text(size = 11, face = "bold", hjust = 0.5)
      )
    
    print(p)
    cat("\n\n")
  }
}

```


# WF plots {.tabset}

## Overlay all scenarios {.tabset .tabset-pills}

```{r wf-overlay, echo=FALSE, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis', eval=RUN_CHUNKS$wf_overlay}
# =============================================================================
# WEIGHT FREQUENCY FITS - ALL SCENARIOS OVERLAID
# =============================================================================

all_fisheries <- unique(unlist(lapply(WeightOut_list, function(x) unique(x@wgtfits$fishery))))

for (fish in all_fisheries) {
  fishery_name <- NULL
  for (sc in names(WeightOut_list)) {
    if (fish %in% unique(WeightOut_list[[sc]]@wgtfits$fishery)) {
      fishery_map <- FISHERY_MAPS[[sc]]
      fishery_name <- get_fishery_name(fish, fishery_map)
      break
    }
  }
  
  if (is.null(fishery_name)) {
    fishery_name <- paste("Fishery", fish)
  }
  
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  combined_data <- map_dfr(names(WeightOut_list), function(sc) {
    df <- WeightOut_list[[sc]]@wgtfits
    if (fish %in% unique(df$fishery)) {
      df %>% 
        filter(fishery == fish) %>% 
        mutate(Scenario = sc)
    } else {
      NULL
    }
  })
  
  if (is.null(combined_data) || nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, weight) %>%
    summarise(obs = sum(obs, na.rm = TRUE), 
              pred = sum(pred, na.rm = TRUE), 
              .groups = "drop") %>%
    filter(obs > 0 | pred > 0)
  
  obs_data <- plot_data %>%
    group_by(year, weight) %>%
    summarise(obs = first(obs), .groups = "drop")
  
  p <- ggplot() +
    geom_col(data = obs_data, 
             aes(x = weight, y = obs, fill = "Observed"), 
             alpha = 0.7, width = 2, position = "identity") +
    geom_line(data = plot_data,
              aes(x = weight, y = pred, color = Scenario), 
              linewidth = 1.2) +
    facet_wrap(~year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(
      title = paste(fishery_name, "- Weight Frequency Fits"),
      x = "Weight (kg)", 
      y = "Frequency"
    ) +
    theme_bw() +
    theme(
      legend.position = "top", 
      legend.box = "vertical",
      strip.text = element_text(size = 8),
      strip.background = element_rect(fill = "grey90"),
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5)
    )
  
  print(p)
  cat("\n\n")
}
```


## By scenario {.tabset .tabset-pills}

```{r wf-by-scenario, echo=FALSE, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis', eval=RUN_CHUNKS$wf_by_scenario}
# =============================================================================
# WEIGHT FREQUENCY FITS BY SCENARIO
# =============================================================================

for (scenario_name in names(WeightOut_list)) {
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- WeightOut_list[[scenario_name]]
  fishery_map <- FISHERY_MAPS[[scenario_name]]
  
  scenario_fisheries <- unique(scenario_data@wgtfits$fishery)
  
  if (length(scenario_fisheries) == 0) {
    cat("*No weight frequency data in this scenario*\n\n")
    next
  }
  
  for (fish in scenario_fisheries) {
    fishery_name <- get_fishery_name(fish, fishery_map)
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    plot_data <- scenario_data@wgtfits %>%
      filter(fishery == fish) %>%
      group_by(fishery, year, weight) %>%
      summarise(obs = sum(obs, na.rm = TRUE), 
                pred = sum(pred, na.rm = TRUE), 
                .groups = "drop") %>%
      filter(obs > 0 | pred > 0)
    
    if (nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    p <- ggplot(plot_data, aes(x = weight)) +
      geom_col(aes(y = obs, fill = "Observed"), 
               alpha = 0.7, width = 2, position = "identity") +
      geom_line(aes(y = pred, color = "Predicted"), linewidth = 1.2) +
      facet_wrap(~year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(
        title = paste(scenario_name, "-", fishery_name, "- Weight Frequency Fits"),
        x = "Weight (kg)", 
        y = "Frequency"
      ) +
      theme_bw() +
      theme(
        legend.position = "top", 
        legend.box = "horizontal",
        strip.text = element_text(size = 8),
        strip.background = element_rect(fill = "grey90"),
        plot.title = element_text(size = 11, face = "bold", hjust = 0.5)
      )
    
    print(p)
    cat("\n\n")
  }
}
```
