---
title: "MFCL outputs"
author: "kyuhan Kim"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: yes
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# =============================================================================
# SETUP BLOCK: Load packages, data, and define global configurations
# This block must be run first. All other blocks depend only on objects
# defined here, making debugging individual sections easier.
# =============================================================================

knitr::opts_chunk$set(
  dev = "png",
  dpi = 160,
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = '../report/Figures/'
)

# -----------------------------------------------------------------------------
# 1. LOAD REQUIRED PACKAGES
# -----------------------------------------------------------------------------
library(ggplot2)
library(cowplot)
library(dplyr)
library(FLR4MFCL)
library(tidyr)
library(patchwork)
library(reshape2)
library(kableExtra)
library(viridis)
library(stringr)
library(purrr)

theme_set(theme_cowplot())

# -----------------------------------------------------------------------------
# 2. LOAD UTILITY FUNCTIONS
# -----------------------------------------------------------------------------
source("../tools/plot_utils.R")

# -----------------------------------------------------------------------------
# 3. CHUNK EVALUATION CONTROL
# Set TRUE/FALSE to enable/disable each section
# -----------------------------------------------------------------------------

RUN_CHUNKS <- list(
  model_summary      = TRUE,   # Model summary table
  bound_hit          = TRUE,   # Bound hit parameter analysis
  spawning_depletion = TRUE,   # SB/SBF0 and recruitment plots
  jitter_analysis    = TRUE,   # Jitter analysis plots
  lik_profile        = TRUE,   # Likelihood profile by component
  piner_lfs          = TRUE,   # Piner plot: Length frequencies

  piner_wfs          = TRUE,   # Piner plot: Weight frequencies
  piner_tag          = TRUE,   # Piner plot: Tagging
  piner_cal_fishery  = TRUE,   # Piner plot: CAL by fishery
  piner_cal_year     = TRUE,   # Piner plot: CAL by year
  cpue_by_scenario   = TRUE,   # CPUE fits by scenario
  cpue_overlay       = FALSE,  # CPUE overlay (interactive)
  lf_overlay         = FALSE,  # LF overlay all scenarios
  lf_by_scenario     = FALSE,  # LF by scenario
  wf_overlay         = FALSE,  # WF overlay all scenarios
  wf_by_scenario     = FALSE   # WF by scenario
)

# -----------------------------------------------------------------------------
# 4. GLOBAL CONFIGURATION
# Centralized configuration for easy modification
# -----------------------------------------------------------------------------

# Paths
MODEL_DIR <- file.path(getwd(), "..", "model")

# Plot aesthetics (named 'config' for compatibility with plot_utils.R functions)
config <- list(
  alpha = 0.7,
  linewidth = 1,
  point_size = 1.5,
  observed_color = "grey30",
  predicted_colors = "coral",
  legend_position = "bottom",
  facet_ncol = 3
)

# Fisheries mapping: maps fishery numbers to descriptive names
ALL_FISHERIES_MAP <- c(
  "1" = "LL-ALL-1", "2" = "LL-ALL-2", "3" = "LL-US-2", "4" = "LL-ALL-3",
  "5" = "LL-OS-3", "6" = "LL-OS-7", "7" = "LL-ALL-7", "8" = "LL-ALL-8",
  "9" = "LL-ALL-4", "10" = "LL-AU-5", "11" = "LL-ALL-5", "12" = "LL-ALL-6",
  "13" = "PS-ASS-3", "14" = "PS-UNA-3", "15" = "PS-ASS-4", "16" = "PS-UNA-4",
  "17" = "MISC-PH-7", "18" = "HL-PHID-7", "19" = "PS-JP-1", "20" = "PL-JP-1",
  "21" = "PL-ALL-3", "22" = "PL-ALL-8", "23" = "MISC-ID-7", "24" = "PS-PHID-7",
  "25" = "PS-ASS-8", "26" = "PS-UNA-8", "27" = "LL-AU-9", "28" = "PL-ALL-7",
  "29" = "LL-ALL-9", "30" = "PS-ASS-7", "31" = "PS-UNA-7", "32" = "MISC-VN-7",
  "33" = "LL-ALL-1i", "34" = "LL-ALL-2i", "35" = "LL-ALL-3i", "36" = "LL-ALL-4i",
  "37" = "LL-ALL-5i", "38" = "LL-ALL-6i", "39" = "LL-ALL-7i", "40" = "LL-ALL-8i",
  "41" = "LL-ALL-9i"
)

# Index fisheries (CPUE fisheries)
INDEX_FISHERIES_MAP <- c(
  "33" = "LL-ALL-1", "34" = "LL-ALL-2", "35" = "LL-ALL-3", "36" = "LL-ALL-4",
  "37" = "LL-ALL-5", "38" = "LL-ALL-6", "39" = "LL-ALL-7", "40" = "LL-ALL-8",
  "41" = "LL-ALL-9"
)

INDEX_FISHERIES <- names(INDEX_FISHERIES_MAP)

# -----------------------------------------------------------------------------
# 4. HELPER FUNCTIONS
# Reusable functions to reduce code duplication
# -----------------------------------------------------------------------------

#' Safely read a file, returning NULL if it doesn't exist
#' @param path File path to read
#' @param reader Function to use for reading (e.g., readLines, read.MFCLPar)
safe_read <- function(path, reader = readLines) {
  if (file.exists(path)) reader(path) else NULL
}

#' Get scenario names that have profiling enabled
#' If run_prof is not in info_list, check if prof_lik_list has data
get_prof_scenarios <- function(info_list, prof_lik_list) {
  # If info_list has run_prof field, use it
  has_run_prof <- sapply(info_list, function(x) !is.null(x$run_prof))
  
  if(any(has_run_prof)) {
    run_prof <- sapply(info_list, function(x) {
      val <- x$run_prof
      if(is.null(val)) return(0)
      as.numeric(val)
    })
    scenarios_with_prof <- names(run_prof)[run_prof == 1]
    return(intersect(names(prof_lik_list), scenarios_with_prof))
  } else {
    # If no run_prof field, just use scenarios that have prof_lik data
    return(names(prof_lik_list))
  }
}

#' Read average biomass values for scenarios
#' @param scenarios Vector of scenario names
#' @param model_dir Base model directory
get_avg_bio <- function(scenarios, model_dir = MODEL_DIR) {
  sapply(scenarios, function(x) {
    # Look for avg_bio in prof/scaler_* folders
    prof_dir <- file.path(model_dir, x, "prof")
    scaler_dirs <- list.dirs(prof_dir, full.names = TRUE, recursive = FALSE)
    scaler_dirs <- grep("scaler_\\d+$", scaler_dirs, value = TRUE)
    
    if (length(scaler_dirs) > 0) {
      # Read from first scaler folder (value should be same across all)
      avg_bio_file <- file.path(scaler_dirs[1], "avg_bio")
      if (file.exists(avg_bio_file)) {
        return(as.numeric(read.table(avg_bio_file)))
      }
    }
    
    # Fallback: try main folder
    avg_bio_file <- file.path(model_dir, x, "avg_bio")
    if (file.exists(avg_bio_file)) {
      return(as.numeric(read.table(avg_bio_file)))
    }
    
    NA_real_
  })
}

#' Convert scaler to biomass units
#' @param scaler Numeric scaler value
#' @param scenario Scenario name
#' @param avg_bio Named vector of average biomass values
scale_to_biomass <- function(scaler, scenario, avg_bio) {
  as.numeric(scaler) * 0.01 * avg_bio[scenario]
}

#' Create a standard likelihood profile plot
#' @param data Data frame with columns: scaler, change, group_var, scenario
#' @param group_var Name of the grouping variable (e.g., "Fishery", "Likelihood")
#' @param label Annotation label for the plot
create_piner_plot <- function(data, group_var, label = NULL) {
  
  # Get unique groups excluding "Total"
  unique_groups <- unique(data[[group_var]])
  non_total_groups <- setdiff(unique_groups, "Total")
  
  # Create color palette
  color_values <- c(
    "Total" = "black",
    setNames(viridis::viridis(length(non_total_groups)), non_total_groups)
  )
  
  p <- ggplot(data, aes(x = scaler, y = change, 
                        colour = .data[[group_var]], 
                        shape = .data[[group_var]])) +
    geom_line(aes(linewidth = .data[[group_var]] == "Total"), alpha = 0.7) +
    geom_point(aes(size = .data[[group_var]] == "Total"), alpha = 0.8) +
    scale_color_manual(values = color_values) +
    scale_linewidth_manual(values = c("TRUE" = 1.5, "FALSE" = 0.7), guide = "none") +
    scale_size_manual(values = c("TRUE" = 3.5, "FALSE" = 2), guide = "none") +
    scale_shape_manual(values = rep(0:24, length.out = length(unique_groups))) +
    facet_wrap(~scenario, scales = "free") +
    scale_x_continuous(
      labels = function(x) x / 1000,
      name = bquote("Average biomass (" * 10^3 * " MT)")
    ) +
    labs(y = "Changes in Likelihood", colour = group_var, shape = group_var) +
    theme(
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 10, face = "bold")
    )
  
  # Add annotation if provided
  if (!is.null(label)) {
    p <- p + annotate("text", x = Inf, y = Inf, label = label,
                      hjust = 1.1, vjust = 1.5, size = 5, fontface = "bold")
  }
  
  return(p)
}

#' Calculate likelihood changes from minimum
#' @param data Data frame with value column
#' @param group_col Name of grouping column
calc_lik_change <- function(data, group_col) {
  data %>%
    group_by(.data[[group_col]], scenario) %>%
    mutate(
      min_value = min(value, na.rm = TRUE),
      change = value - min_value
    ) %>%
    ungroup()
}

#' Parse indepvar.rpt file
#' @param lines Character vector of file lines
parse_indepvar <- function(lines) {
  if (is.null(lines) || length(lines) < 2) return(NULL)
  
  data_list <- lapply(2:length(lines), function(i) {
    line <- lines[i]
    if (nchar(trimws(line)) == 0) return(NULL)
    
    hit_bound <- grepl("\\*{5,}", line)
    line_clean <- gsub("\\*+", "", line)
    parts <- strsplit(trimws(line_clean), "\\s+")[[1]]
    
    if (length(parts) >= 6) {
      data.frame(
        Index = as.integer(parts[1]),
        Var_name = parts[2],
        Estimate = as.numeric(parts[3]),
        L_bound = as.numeric(parts[4]),
        U_bound = as.numeric(parts[5]),
        Gradient = as.numeric(parts[6]),
        Hit_Bound = hit_bound,
        stringsAsFactors = FALSE
      )
    } else {
      NULL
    }
  })
  
  do.call(rbind, Filter(Negate(is.null), data_list))
}

#' Get fishery name from number
get_fishery_name <- function(fishery_num, mapping = ALL_FISHERIES_MAP) {
  name <- mapping[as.character(fishery_num)]
  if (is.na(name)) paste("Fishery", fishery_num) else name
}

#' Generate scenario color palette
get_scenario_colors <- function(scenarios, option = "D") {
  setNames(viridis(length(scenarios), option = option, direction = 1), scenarios)
}

# -----------------------------------------------------------------------------
# 5. LOAD MODEL DATA
# Read all model outputs into organized lists
# -----------------------------------------------------------------------------

# Get all model folders
model_folders <- list.dirs(MODEL_DIR, full.names = TRUE, recursive = FALSE)
model_names <- basename(model_folders)

# Load data from each model folder
results <- setNames(lapply(model_folders, function(folder) {
  cat("Processing folder:", folder, "\n")
  
  # Read core model outputs
  par_out <- read.MFCLPar(finalPar(folder))
  rep_out <- read.MFCLRep(finalRep(folder))
  len_out <- read.MFCLLenFit(file.path(folder, "length.fit"))
  wgt_out <- read.MFCLWgtFit(file.path(folder, "weight.fit"))
  tag_out <- read.MFCLTag(list.files(folder, "\\.tag$", full.names = TRUE))
  age_out <- read.MFCLALK(list.files(folder, "\\.age_length$", full.names = TRUE))
  
  
  # Read optional files
  indep_out <- safe_read(file.path(folder, "indepvar.rpt"))
  info <- readRDS(file.path(folder, "model_info.rds"))
  
  # Read likelihood profile outputs from prof/scaler_* subdirectories
  prof_dir <- file.path(folder, "prof")
  all_dirs <- list.dirs(prof_dir, full.names = TRUE, recursive = FALSE)
  scaler_dirs <- grep("scaler_\\d+$", all_dirs, value = TRUE)
  
  if (length(scaler_dirs) > 0) {
    # Extract scaler values from directory names
    scales <- basename(scaler_dirs) %>% str_extract("\\d+$")
    
    # Read test_plot_output from each scaler directory
    output_files <- file.path(scaler_dirs, "test_plot_output")
    
    # Filter only existing files
    existing_files <- output_files[file.exists(output_files)]
    existing_scales <- scales[file.exists(output_files)]
    
    if (length(existing_files) > 0) {
      lik_out <- setNames(map(existing_files, read.MFCLLikelihood), existing_scales)
      lik_raw <- setNames(map(existing_files, readLines), existing_scales)
    } else {
      lik_out <- list()
      lik_raw <- list()
      existing_scales <- character(0)
    }
  } else {
    # Fallback: try old format (test_plot_output_XX files in main folder)
    output_files <- list.files(folder, pattern = "^test_plot_output_\\d+$", full.names = TRUE)
    
    if (length(output_files) > 0) {
      scales <- basename(output_files) %>% str_extract("\\d+$")
      lik_out <- setNames(map(output_files, read.MFCLLikelihood), scales)
      lik_raw <- setNames(map(output_files, readLines), scales)
      existing_scales <- scales
    } else {
      lik_out <- list()
      lik_raw <- list()
      existing_scales <- character(0)
    }
  }
  
  # Read jitter outputs from jitter/jitter_seed_* subdirectories
  jitter_dir <- file.path(folder, "jitter")
  jitter_seed_dirs <- list.dirs(jitter_dir, full.names = TRUE, recursive = FALSE)
  jitter_seed_dirs <- grep("jitter_seed_\\d+$", jitter_seed_dirs, value = TRUE)
  
  if (length(jitter_seed_dirs) > 0) {
    seeds <- basename(jitter_seed_dirs) %>% str_extract("\\d+$")
    
    # Read par files from each jitter seed directory
    jitter_pars <- setNames(map(jitter_seed_dirs, function(d) {
      par_file <- list.files(d, pattern = "jittered_out_\\d+\\.par$", full.names = TRUE)
      if (length(par_file) > 0) {
        tryCatch(read.MFCLPar(par_file[1]), error = function(e) NULL)
      } else {
        NULL
      }
    }), seeds)
    
    # Read jitter info
    jitter_infos <- setNames(map(jitter_seed_dirs, function(d) {
      info_file <- file.path(d, "jitter_info.rds")
      if (file.exists(info_file)) readRDS(info_file) else NULL
    }), seeds)
    
    # Filter out NULLs
    jitter_pars <- Filter(Negate(is.null), jitter_pars)
    jitter_infos <- Filter(Negate(is.null), jitter_infos)
  } else {
    jitter_pars <- list()
    jitter_infos <- list()
  }
  
  list(
    ParOut = par_out, RepOut = rep_out, LengOut = len_out, WeightOut = wgt_out,
    TagOut = tag_out, AgeOut = age_out, LikOut = lik_out, LikRawOut = lik_raw,
    scales = existing_scales, IndepOut = indep_out, info = info,
    JitterPars = jitter_pars, JitterInfos = jitter_infos
  )
}), model_names)
# -----------------------------------------------------------------------------
# 6. EXTRACT DATA INTO NAMED LISTS FOR EASY ACCESS
# Each list is named by model/scenario name
# -----------------------------------------------------------------------------

ParOut_list <- map(results, "ParOut")
RepOut_list <- map(results, "RepOut")
LengOut_list <- map(results, "LengOut")
WeightOut_list <- map(results, "WeightOut")
TagOut_list <- map(results, "TagOut")
AgeOut_list <- map(results, "AgeOut")
IndepOut_list <- map(results, "IndepOut")
Info_list <- map(results, "info")
ProfLikOut_list <- map(results, "LikOut")
ProfLikOutRaw_list <- map(results, "LikRawOut")
JitterPars_list <- map(results, "JitterPars")
JitterInfos_list <- map(results, "JitterInfos")

# Extract year range from first model
minYear <- ParOut_list[[1]]@range["minyear"]
maxYear <- ParOut_list[[1]]@range["maxyear"]

# Create tag program mapping for each model
tag_program_maps <- map(TagOut_list, ~ {
  .x@releases %>%
    distinct(rel.group, program) %>%
    rename(program_name = program)
})

```


# Summary of each model configuration

```{r model-summary, echo=FALSE, message=FALSE, fig.dim=c(10,10), eval=RUN_CHUNKS$model_summary}
# =============================================================================
# MODEL SUMMARY TABLE
# Extracts key parameters from each model for comparison
# =============================================================================

# Extract parameters from each model
params_df <- imap_dfr(ParOut_list, function(par, model_name) {
  
  # Safely extract values with error handling
  get_slot <- function(slot_name, default = NA) {
    tryCatch(slot(par, slot_name), error = function(e) default)
  }
  
  dims <- tryCatch(
    as.list(par@dimensions),
    error = function(e) list(
      agecls = NA, years = NA, seasons = NA,
      regions = NA, fisheries = NA, taggrps = NA
    )
  )
  
  data.frame(
    Model = model_name,
    mgc = round(as.numeric(get_slot("max_grad")), 6),
    obj_fun = round(as.numeric(get_slot("obj_fun")), 2),
    n_pars = as.numeric(get_slot("n_pars")),
    agecls = dims$agecls,
    years = dims$years,
    seasons = dims$seasons,
    regions = dims$regions,
    fisheries = dims$fisheries,
    taggrps = dims$taggrps
  )
})

# Display table
kable(params_df, caption = "Basic model info") %>%
  kable_styling(full_width = FALSE)
```


# Bound Hit Parameter Analysis {.tabset .tabset-pills}

```{r bound-hit-analysis, echo=FALSE, message=FALSE, warning=FALSE, results='asis', eval=RUN_CHUNKS$bound_hit}
# =============================================================================
# BOUND HIT ANALYSIS
# Identifies parameters that hit their bounds during optimization
# =============================================================================

# Separate models with and without indepvar.rpt
null_models <- names(IndepOut_list)[sapply(IndepOut_list, is.null)]
valid_models <- names(IndepOut_list)[!sapply(IndepOut_list, is.null)]

# Process each valid model
model_results <- map(setNames(valid_models, valid_models), function(model_name) {
  
  df <- parse_indepvar(IndepOut_list[[model_name]])
  if (is.null(df)) return(NULL)
  
  # Calculate distances to bounds
  df <- df %>%
    mutate(
      Distance_to_lower = abs(Estimate - L_bound),
      Distance_to_upper = abs(Estimate - U_bound),
      Hit_Type = case_when(
        !Hit_Bound ~ "None",
        Distance_to_lower <= Distance_to_upper ~ "Lower",
        TRUE ~ "Upper"
      ),
      Distance_to_bound = if_else(
        Hit_Bound,
        if_else(Hit_Type == "Lower", Distance_to_lower, Distance_to_upper),
        NA_real_
      ),
      Var_type = str_extract(Var_name, "^[a-zA-Z_]+")
    )
  
  # Extract bound hits
  bound_hits <- df %>%
    filter(Hit_Bound) %>%
    select(Index, Var_name, Var_type, Estimate, Hit_Type,
           L_bound, U_bound, Distance_to_bound, Gradient) %>%
    arrange(Index)
  
  # Save to CSV
  write.csv(bound_hits, paste0("bound_hits_", model_name, ".csv"), row.names = FALSE)
  
  list(total_params = nrow(df), bound_hits = bound_hits)
})

# Remove NULL results
model_results <- Filter(Negate(is.null), model_results)

# --- Overview Tab ---
cat("\n## Overview\n\n")

cat(sprintf("**Total Models:** %d  \n", length(IndepOut_list)))
cat(sprintf("**Models with indepvar.rpt:** %d  \n", length(valid_models)))
cat(sprintf("**Models without indepvar.rpt:** %d  \n\n", length(null_models)))

if (length(model_results) > 0) {
  overview <- data.frame(
    Model = names(model_results),
    Total_Params = sapply(model_results, function(x) x$total_params),
    Bound_Hits = sapply(model_results, function(x) nrow(x$bound_hits)),
    Hit_Rate = sapply(model_results, function(x) 
      sprintf("%.2f%%", nrow(x$bound_hits) / x$total_params * 100)),
    Lower_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Lower")),
    Upper_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Upper"))
  )
  
  print(
    kable(overview,
          col.names = c("Model", "Total", "Hits", "Rate", "Lower", "Upper"),
          align = c("l", "r", "r", "r", "r", "r"),
          row.names = FALSE) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE) %>%
      row_spec(0, bold = TRUE, background = "#2196F3", color = "white") %>%
      column_spec(3, bold = TRUE, color = "red")
  )
}

# List models without indepvar.rpt
if (length(null_models) > 0) {
  cat("\n\n### Models Without indepvar.rpt\n\n")
  cat("The following models did not generate an `indepvar.rpt` file:\n\n")
  for (model in null_models) {
    cat(sprintf("- **%s**: `indepvar.rpt` was not generated\n", model))
  }
  cat("\n")
}

# --- Individual Model Tabs ---
for (model_name in names(model_results)) {
  result <- model_results[[model_name]]
  bound_hits <- result$bound_hits
  
  cat(sprintf("\n## %s\n\n", model_name))
  
  cat(sprintf("**Total Parameters:** %s  \n", format(result$total_params, big.mark = ",")))
  cat(sprintf("**Bound Hits:** %d (%.2f%%)  \n", 
              nrow(bound_hits), nrow(bound_hits) / result$total_params * 100))
  cat(sprintf("**Lower Bound Hits:** %d  \n", sum(bound_hits$Hit_Type == "Lower")))
  cat(sprintf("**Upper Bound Hits:** %d  \n\n", sum(bound_hits$Hit_Type == "Upper")))
  
  if (nrow(bound_hits) > 0) {
    cat("### Bound Hit Parameters\n\n")
    
    bound_hits_display <- bound_hits %>%
      mutate(
        Estimate_fmt = sprintf("%.4e", Estimate),
        Distance_fmt = sprintf("%.2e", Distance_to_bound)
      ) %>%
      select(Index, Var_name, Var_type, Estimate_fmt, Hit_Type, 
             L_bound, U_bound, Distance_fmt)
    
    print(
      kable(bound_hits_display,
            col.names = c("Index", "Parameter", "Type", "Estimate", "Hit",
                          "Lower", "Upper", "Distance"),
            align = c("r", "l", "l", "r", "c", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                      full_width = TRUE, font_size = 11) %>%
        row_spec(0, bold = TRUE, background = "#4CAF50", color = "white") %>%
        column_spec(5, bold = TRUE,
                    color = ifelse(bound_hits$Hit_Type == "Lower", "#E74C3C", "#3498DB")) %>%
        scroll_box(width = "100%", height = "400px")
    )
    
    cat("\n\n### Summary by Variable Type\n\n")
    
    type_summary <- bound_hits %>%
      count(Var_type, Hit_Type) %>%
      pivot_wider(names_from = Hit_Type, values_from = n, values_fill = 0) %>%
      mutate(Total = Lower + Upper) %>%
      arrange(desc(Total))
    
    print(
      kable(type_summary,
            col.names = c("Type", "Lower", "Upper", "Total"),
            align = c("l", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover"),
                      full_width = FALSE) %>%
        row_spec(0, bold = TRUE, background = "#FF9800", color = "white") %>%
        column_spec(4, bold = TRUE)
    )
    
    cat(sprintf("\n\n*Data saved to: `bound_hits_%s.csv`*\n\n", model_name))
  } else {
    cat("\n✅ **No bound hits detected in this model**\n\n")
  }
}

# --- NULL Model Tabs ---
for (model_name in null_models) {
  cat(sprintf("\n## %s\n\n", model_name))
  cat("⚠️ **No `indepvar.rpt` file.**\n\n")
}
```


# Spawning depletion

```{r spawning-depletion, echo=FALSE, message=FALSE, fig.dim=c(8,6), eval=RUN_CHUNKS$spawning_depletion}
# =============================================================================
# SPAWNING BIOMASS DEPLETION AND RECRUITMENT PLOTS
# =============================================================================

# Extract spawning biomass depletion and recruitment
SBdep <- GetQuantSimple(SBSBF0, RepOut_list, minYear, maxYear)
Rec <- GetQuantSimple(eq_rec, RepOut_list, minYear, maxYear, scale_factor = 1/1e6)

# Define color palette
scenario_levels <- unique(SBdep$Scenario)
scenario_colors <- get_scenario_colors(scenario_levels)

# Convert to factor for consistent ordering
SBdep$Scenario <- factor(SBdep$Scenario, levels = scenario_levels)
Rec$Scenario <- factor(Rec$Scenario, levels = scenario_levels)

# Common theme for both plots
common_theme <- theme_bw() + theme(legend.position = "none")

# Plot 1: SB/SBF=0
SBdepPlot <- ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) +
  geom_line(linewidth = 1.2) +
  scale_color_manual(values = scenario_colors) +
  labs(x = "Year", y = bquote(SB/SB["F=0"])) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "darkred") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgreen") +
  common_theme

# Plot 2: Recruitment
RecPlot <- ggplot(Rec, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) +
  geom_line(linewidth = 1.2) +
  coord_cartesian(ylim = c(0, NA)) +
  scale_color_manual(values = scenario_colors) +
  labs(x = "Year", y = bquote("Spawning Potential (" * 10^3 * " MT)")) +
  common_theme

# Extract legend from a temporary plot
legend <- cowplot::get_legend(
  ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario)) +
    geom_line(linewidth = 2) +
    scale_color_manual(values = scenario_colors) +
    theme_bw() +
    theme(
      legend.position = "right",
      legend.title = element_text(face = "bold"),
      legend.key.width = unit(1.5, "cm")
    ) +
    labs(color = "Scenario")
)

# Combine plots
combined_plot <- cowplot::plot_grid(
  SBdepPlot, RecPlot,
  ncol = 1, labels = c("A", "B"), label_size = 12, align = "v"
)

final_plot <- cowplot::plot_grid(
  combined_plot, legend,
  ncol = 2, rel_widths = c(4, 1)
)

print(final_plot)
```


# Jitter Analysis {.tabset}

```{r jitter-analysis, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.dim=c(12,8), eval=RUN_CHUNKS$jitter_analysis}
# Get scenarios with jitter runs
scenarios_with_jitter <- names(JitterPars_list)[sapply(JitterPars_list, function(x) length(x) > 0)]

if (length(scenarios_with_jitter) > 0) {
  
  # Collect all data including max_grad
  all_jitter_data <- list()
  
  for (scenario in scenarios_with_jitter) {
    jitter_pars <- JitterPars_list[[scenario]]
    base_par <- ParOut_list[[scenario]]
    seeds <- names(jitter_pars)
    
    if (length(seeds) == 0) next
    
    ref_obj <- as.numeric(base_par@obj_fun)
    ref_grad <- base_par@max_grad
    
    jitter_obj <- sapply(jitter_pars, function(p) as.numeric(p@obj_fun))
    jitter_grad <- sapply(jitter_pars, function(p) p@max_grad)
    
    # Percent difference from reference
    pct_diff <- ((jitter_obj - ref_obj) / abs(ref_obj)) * 100
    
    all_jitter_data[[scenario]] <- data.frame(
      scenario = scenario,
      obj_fun = jitter_obj,
      ref_obj = ref_obj,
      pct_diff = pct_diff,
      max_grad = jitter_grad,
      ref_grad = ref_grad,
      jitter_id = seq_along(jitter_grad)
    )
  }
  
  # Combine all data
  plot_df <- do.call(rbind, all_jitter_data)
  
  # Identify outliers
  plot_df <- plot_df %>%
    mutate(
      is_outlier = pct_diff < -5 | pct_diff > 20,
      outlier_direction = case_when(
        pct_diff < -5 ~ "below",
        pct_diff > 20 ~ "above",
        TRUE ~ "none"
      )
    )
  
  # Create reference model dataframe
  ref_df <- plot_df %>%
    group_by(scenario) %>%
    slice(1) %>%
    select(scenario, ref_obj, ref_grad)
  
  # Separate outliers
  outliers_df <- plot_df %>% filter(is_outlier)
  
  # Scatter plot with jitter_id as continuous color
  p <- ggplot(plot_df %>% filter(!is_outlier), aes(x = max_grad, y = pct_diff)) +
    geom_point(aes(color = jitter_id), size = 3, alpha = 0.7) +
    # Outliers at plot edges with arrows
    geom_point(data = outliers_df %>% filter(outlier_direction == "above"),
               aes(x = max_grad, y = 19.5), 
               color = "orange", size = 3, shape = 24, fill = "orange") +
    geom_point(data = outliers_df %>% filter(outlier_direction == "below"),
               aes(x = max_grad, y = -4.5), 
               color = "orange", size = 3, shape = 25, fill = "orange") +
    geom_point(data = ref_df, aes(x = ref_grad, y = 0), 
               color = "red", size = 5, shape = 18) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8, alpha = 0.5) +
    geom_vline(xintercept = 0.001, linetype = "dotted", color = "gray50", linewidth = 0.6) +
    scale_color_viridis_c(option = "viridis", 
                          name = "Jitter ID") +
    scale_x_log10() +
    coord_cartesian(ylim = c(-5, 20)) +
    facet_wrap(~scenario, scales = "free_x", ncol = 2) +
    labs(x = "Maximum Gradient (log scale)", 
         y = "% Difference in Objective Function",
         title = "Jitter Analysis: Convergence Diagnostics",
         subtitle = "Red diamond = Reference Model | Gray line = 0.001 reference | Orange triangles = Outliers") +
    theme_bw() +
    theme(plot.title = element_text(size = 14, face = "bold"),
          strip.text = element_text(size = 11, face = "bold"),
          strip.background = element_rect(fill = "lightblue"),
          legend.position = "right")
  
  print(p)
  
  cat("\\n\\n")
  
  # Summary table
  cat("### Summary Statistics\\n\\n")
  
  summary_list <- lapply(split(plot_df, plot_df$scenario), function(df) {
    data.frame(
      scenario = unique(df$scenario),
      ref_obj = sprintf("%.2f", unique(df$ref_obj)),
      ref_grad = sprintf("%.4f", unique(df$ref_grad)),
      n_jitter = nrow(df),
      pct_diff_min = sprintf("%.2f%%", min(df$pct_diff)),
      pct_diff_median = sprintf("%.2f%%", median(df$pct_diff)),
      pct_diff_max = sprintf("%.2f%%", max(df$pct_diff)),
      grad_min = sprintf("%.4f", min(df$max_grad)),
      grad_median = sprintf("%.4f", median(df$max_grad)),
      grad_max = sprintf("%.4f", max(df$max_grad)),
      n_outliers_above = sum(df$pct_diff > 20),
      n_outliers_below = sum(df$pct_diff < -5)
    )
  })
  
  summary_df <- do.call(rbind, summary_list)
  rownames(summary_df) <- NULL
  
  print(
    kable(summary_df,
          col.names = c("Scenario", "Ref Obj", "Ref Grad", "N", 
                        "% Diff Min", "% Diff Med", "% Diff Max",
                        "Grad Min", "Grad Med", "Grad Max", 
                        "Outliers ▲", "Outliers ▼"),
          align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r")) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE) %>%
      row_spec(0, bold = TRUE, background = "#673AB7", color = "white")
  )
  
} else {
  cat("*No jitter analysis results found in any model folder.*\\n\\n")
}
```

# Likelihood profile {.tabset}

## Each component

```{r lik-profile-components, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$lik_profile}
# =============================================================================
# LIKELIHOOD PROFILE BY COMPONENT
# Shows how each likelihood component changes across biomass scalers
# =============================================================================

# Get scenarios with profiling enabled
scenarios_prof <- get_prof_scenarios(Info_list, ProfLikOut_list)

if (length(scenarios_prof) > 0) {
  
  # Get average biomass for scaling
  avg_bio <- get_avg_bio(scenarios_prof)
  
  # Get scales from first result (assumes same across all)
  scales <- results[[scenarios_prof[1]]]$scales
  
  # Extract likelihood components for each scale
  Likes <- map(scales, function(scl) {
    # Extract components for each scenario
    mat <- sapply(scenarios_prof, function(sc) {
      lik <- ProfLikOut_list[[sc]][[scl]]
      raw <- ProfLikOutRaw_list[[sc]][[scl]]
      
      c(
        Indices = sum(lik@survey_index),
        LFs = sum(lik@total_length_fish),
        Penalties = as.numeric(raw[6]),
        WFs = sum(lik@total_weight_fish),
        Age = sum(lik@age_length),
        Tags = sum(unlist(lik@tag_rel_fish, recursive = TRUE))
      )
    })
    
    # Add Total row
    rbind(mat, Total = colSums(mat))
  })
  names(Likes) <- scales
  
  # Convert to long format
  Likes_long <- imap_dfr(Likes, function(mat, scl) {
    as.data.frame(mat) %>%
      tibble::rownames_to_column("Likelihood") %>%
      mutate(scaler = scl)
  }) %>%
    pivot_longer(cols = all_of(scenarios_prof), names_to = "scenario", values_to = "value") %>%
    mutate(scaler = scale_to_biomass(scaler, scenario, avg_bio))
  
  # Calculate change from minimum
  Likes_change <- calc_lik_change(Likes_long, "Likelihood")
  
  # Create plot
  print(create_piner_plot(Likes_change, "Likelihood"))
}
```



## Piner (CPUEs)

```{r piner-CPUEs, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_lfs}
# =============================================================================
# PINER PLOT: INDEX CPUE LIKELIHOODS BY FISHERY
# =============================================================================

scenarios_prof <- get_prof_scenarios(Info_list, ProfLikOut_list)

if (length(scenarios_prof) > 0) {
  
  avg_bio <- get_avg_bio(scenarios_prof)
  scales <- results[[scenarios_prof[1]]]$scales
  
  Likes <- map(scales, function(scl) {
    mat <- sapply(scenarios_prof, function(sc) {
      cpue_vec <- ProfLikOutRaw_list[[sc]][[scl]][68] %>%  
        strsplit(" ") %>%
        unlist() %>% 
        as.numeric() %>%
        na.omit()
      names(cpue_vec) <- INDEX_FISHERIES_MAP[as.character(seq_along(cpue_vec))]
      cpue_vec
    })
    
    # Remove zero rows and add total
    mat <- mat[rowSums(mat != 0) > 0, , drop = FALSE]
    rbind(mat, Total = colSums(mat))
  })
  
  # Convert to long format
  Likes_long <- imap_dfr(Likes, function(mat, scl) {
    as.data.frame(mat) %>%
      tibble::rownames_to_column("Fishery") %>%
      mutate(scaler = scl)
  }) %>%
    pivot_longer(cols = all_of(scenarios_prof), names_to = "scenario", values_to = "value") %>%
    mutate(scaler = scale_to_biomass(scaler, scenario, avg_bio))
  
  # Calculate change and plot
  Likes_change <- calc_lik_change(Likes_long, "Fishery")
  print(create_piner_plot(Likes_change, "Fishery", "CPUEs"))
}

```



## Piner (LFs)

```{r piner-lfs, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_lfs}
# =============================================================================
# PINER PLOT: LENGTH FREQUENCY LIKELIHOODS BY FISHERY
# =============================================================================

scenarios_prof <- get_prof_scenarios(Info_list, ProfLikOut_list)

if (length(scenarios_prof) > 0) {
  
  avg_bio <- get_avg_bio(scenarios_prof)
  scales <- results[[scenarios_prof[1]]]$scales
  
  # Extract LF likelihoods by fishery
  Likes <- map(scales, function(scl) {
    mat <- sapply(scenarios_prof, function(sc) {
      lf_vec <- ProfLikOut_list[[sc]][[scl]]@total_length_fish
      names(lf_vec) <- ALL_FISHERIES_MAP[as.character(seq_along(lf_vec))]
      lf_vec
    })
    
    # Remove zero rows and add total
    mat <- mat[rowSums(mat != 0) > 0, , drop = FALSE]
    rbind(mat, Total = colSums(mat))
  })
  names(Likes) <- scales
  
  # Convert to long format
  Likes_long <- imap_dfr(Likes, function(mat, scl) {
    as.data.frame(mat) %>%
      tibble::rownames_to_column("Fishery") %>%
      mutate(scaler = scl)
  }) %>%
    pivot_longer(cols = all_of(scenarios_prof), names_to = "scenario", values_to = "value") %>%
    mutate(scaler = scale_to_biomass(scaler, scenario, avg_bio))
  
  # Calculate change and plot
  Likes_change <- calc_lik_change(Likes_long, "Fishery")
  print(create_piner_plot(Likes_change, "Fishery", "LFs"))
}
```

## Piner (WFs)

```{r piner-wfs, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_wfs}
# =============================================================================
# PINER PLOT: WEIGHT FREQUENCY LIKELIHOODS BY FISHERY
# =============================================================================

scenarios_prof <- get_prof_scenarios(Info_list, ProfLikOut_list)

if (length(scenarios_prof) > 0) {
  
  avg_bio <- get_avg_bio(scenarios_prof)
  scales <- results[[scenarios_prof[1]]]$scales
  
  # Extract WF likelihoods by fishery
  Likes <- map(scales, function(scl) {
    mat <- sapply(scenarios_prof, function(sc) {
      wf_vec <- ProfLikOut_list[[sc]][[scl]]@total_weight_fish
      names(wf_vec) <- ALL_FISHERIES_MAP[as.character(seq_along(wf_vec))]
      wf_vec
    })
    
    mat <- mat[rowSums(mat != 0) > 0, , drop = FALSE]
    rbind(mat, Total = colSums(mat))
  })
  names(Likes) <- scales
  
  # Convert to long format
  Likes_long <- imap_dfr(Likes, function(mat, scl) {
    as.data.frame(mat) %>%
      tibble::rownames_to_column("Fishery") %>%
      mutate(scaler = scl)
  }) %>%
    pivot_longer(cols = all_of(scenarios_prof), names_to = "scenario", values_to = "value") %>%
    mutate(scaler = scale_to_biomass(scaler, scenario, avg_bio))
  
  Likes_change <- calc_lik_change(Likes_long, "Fishery")
  print(create_piner_plot(Likes_change, "Fishery", "WFs"))
}
```

## Piner (Tagging)

```{r piner-tag, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_tag}
# =============================================================================
# PINER PLOT: TAGGING LIKELIHOODS BY PROGRAM
# =============================================================================

scenarios_prof <- get_prof_scenarios(Info_list, ProfLikOut_list)

if (length(scenarios_prof) > 0) {
  
  avg_bio <- get_avg_bio(scenarios_prof)
  scales <- results[[scenarios_prof[1]]]$scales
  
  # Extract tag likelihoods by program
  Likes_raw <- map(scales, function(scl) {
    sapply(scenarios_prof, function(sc) {
      tag_rel <- ProfLikOut_list[[sc]][[scl]]@tag_rel_fish
      sums_vec <- sapply(tag_rel, function(g) sum(unlist(g)))
      names(sums_vec) <- tag_program_maps[[sc]]$program_name[seq_along(sums_vec)]
      sums_vec
    }, simplify = FALSE)
  })
  names(Likes_raw) <- scales
  
  # Convert to data frame
  Likes_long <- bind_rows(lapply(names(Likes_raw), function(scl) {
    bind_rows(lapply(names(Likes_raw[[scl]]), function(sc) {
      vec <- Likes_raw[[scl]][[sc]]
      data.frame(scenario = sc, scaler = scl, program = names(vec), value = as.numeric(vec))
    }))
  })) %>%
    mutate(scaler = scale_to_biomass(scaler, scenario, avg_bio)) %>%
    group_by(program, scaler, scenario) %>%
    summarise(value = sum(value), .groups = "drop")
  
  # Add total
  Likes_total <- Likes_long %>%
    group_by(scaler, scenario) %>%
    summarise(value = sum(value), .groups = "drop") %>%
    mutate(program = "Total")
  
  Likes_long <- bind_rows(Likes_long, Likes_total)
  
  Likes_change <- calc_lik_change(Likes_long, "program")
  print(create_piner_plot(Likes_change, "program", "Tagging program"))
}
```

## Piner (CAL by fishery)

```{r piner-cal-fishery, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_cal_fishery}
# =============================================================================
# PINER PLOT: CONDITIONAL AGE-AT-LENGTH BY FISHERY
# =============================================================================

scenarios_prof <- names(ProfLikOut_list)
avg_bio <- get_avg_bio(scenarios_prof)

# Extract CAL likelihood data for all scenarios
age_lik_data <- map_dfr(scenarios_prof, function(sc) {
  
  # Get unique year-month-fishery combinations
  alk_summary <- as.data.frame(AgeOut_list[[sc]]@ALK) %>%
    mutate(order = row_number()) %>%
    group_by(year, month, fishery) %>%
    summarise(first_order = min(order), .groups = "drop") %>%
    arrange(first_order) %>%
    select(-first_order)
  
  # Get scalers
  scalers <- names(ProfLikOut_list[[sc]])
  
  # Add likelihood values for each scaler
  map_dfr(scalers, function(scl) {
    lik_vec <- ProfLikOut_list[[sc]][[scl]]@age_length
    alk_summary %>%
      mutate(
        scenario = sc,
        scaler = scale_to_biomass(scl, sc, avg_bio),
        Lik = lik_vec[seq_len(nrow(alk_summary))]
      )
  })
})

# Map fishery numbers to names
age_lik_data <- age_lik_data %>%
  mutate(fishery = ALL_FISHERIES_MAP[as.character(fishery)])

# Sum by fishery
lik_by_fishery <- age_lik_data %>%
  group_by(fishery, scaler, scenario) %>%
  summarise(value = sum(Lik, na.rm = TRUE), .groups = "drop")

# Add total
lik_total <- lik_by_fishery %>%
  group_by(scaler, scenario) %>%
  summarise(value = sum(value), .groups = "drop") %>%
  mutate(fishery = "Total")

lik_combined <- bind_rows(lik_by_fishery, lik_total)

lik_change <- lik_combined %>%
  group_by(fishery, scenario) %>%
  mutate(change = value - min(value, na.rm = TRUE)) %>%
  ungroup()

print(create_piner_plot(lik_change, "fishery", "CAL"))
```

## Piner (CAL by year)

```{r piner-cal-year, echo=FALSE, message=FALSE, fig.dim=c(8,8), eval=RUN_CHUNKS$piner_cal_year}
# =============================================================================
# PINER PLOT: CONDITIONAL AGE-AT-LENGTH BY YEAR
# =============================================================================

scenarios_prof <- names(ProfLikOut_list)
avg_bio <- get_avg_bio(scenarios_prof)

# Extract CAL likelihood data (reuse from previous chunk if in same session)
age_lik_data <- map_dfr(scenarios_prof, function(sc) {
  
  alk_summary <- as.data.frame(AgeOut_list[[sc]]@ALK) %>%
    mutate(order = row_number()) %>%
    group_by(year, month, fishery) %>%
    summarise(first_order = min(order), .groups = "drop") %>%
    arrange(first_order) %>%
    select(-first_order)
  
  scalers <- names(ProfLikOut_list[[sc]])
  
  map_dfr(scalers, function(scl) {
    lik_vec <- ProfLikOut_list[[sc]][[scl]]@age_length
    alk_summary %>%
      mutate(
        scenario = sc,
        scaler = scale_to_biomass(scl, sc, avg_bio),
        Lik = lik_vec[seq_len(nrow(alk_summary))]
      )
  })
})

# Sum by year
lik_by_year <- age_lik_data %>%
  group_by(year, scaler, scenario) %>%
  summarise(value = sum(Lik, na.rm = TRUE), .groups = "drop")

# Add total
lik_total <- lik_by_year %>%
  group_by(scaler, scenario) %>%
  summarise(value = sum(value), .groups = "drop") %>%
  mutate(year = "Total")

lik_combined <- bind_rows(
  lik_by_year %>% mutate(year = as.character(year)),
  lik_total
)

lik_change <- lik_combined %>%
  group_by(year, scenario) %>%
  mutate(change = value - min(value, na.rm = TRUE)) %>%
  ungroup()

print(create_piner_plot(lik_change, "year", "CAL"))
```


# CPUE plots {.tabset}

## Observed vs Fitted CPUE by scenario {.tabset .tabset-pills}

```{r cpue-by-scenario, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.dim=c(8,8), eval=RUN_CHUNKS$cpue_by_scenario}
# =============================================================================
# CPUE FITS BY SCENARIO
# Uses create_cpue_plots from plot_utils.R
# =============================================================================

# Create plots using utility function
scenario_plots <- create_cpue_plots(
  RepOut_list = RepOut_list,
  fisheries = INDEX_FISHERIES,
  fisheries_mapping = INDEX_FISHERIES_MAP,
  viridis_option = "viridis"
)

# Print each scenario in its own tab
for (nm in names(scenario_plots)) {
  cat(sprintf("\n### %s\n\n", nm))
  print(scenario_plots[[nm]])
  cat("\n\n")
}
```

## Overlay all scenarios (Interactive)

```{r cpue-overlay, echo=FALSE, message=FALSE, fig.dim=c(10,8), eval=RUN_CHUNKS$cpue_overlay}
# =============================================================================
# CPUE FITS - ALL SCENARIOS OVERLAID (Interactive)
# =============================================================================

library(plotly)

overlay_plot <- create_overlay_cpue_plot(
  RepOut_list = RepOut_list,
  fisheries = INDEX_FISHERIES,
  fisheries_mapping = INDEX_FISHERIES_MAP,
  viridis_option = "viridis",
  custom_config = list(predicted_colors = NULL)
)

interactive_plot <- ggplotly(overlay_plot, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(
      orientation = "v", x = 1.02, y = 1,
      xanchor = "left", yanchor = "top"
    )
  )

interactive_plot
```


# LF plots {.tabset}

## Overlay all scenarios {.tabset .tabset-pills}

```{r lf-overlay, echo=FALSE, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis', eval=RUN_CHUNKS$lf_overlay}
# =============================================================================
# LENGTH FREQUENCY FITS - ALL SCENARIOS OVERLAID
# =============================================================================

# Get all unique fisheries
all_fisheries <- unique(unlist(lapply(LengOut_list, function(x) unique(x@lenfits$fishery))))

for (fish in all_fisheries) {
  fishery_name <- get_fishery_name(fish)
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  # Combine data from all scenarios
  combined_data <- map_dfr(names(LengOut_list), function(sc) {
    df <- LengOut_list[[sc]]@lenfits
    if (fish %in% unique(df$fishery)) {
      df %>% filter(fishery == fish) %>% mutate(Scenario = sc)
    } else {
      NULL
    }
  })
  
  if (nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, length) %>%
    summarise(obs = sum(obs), pred = sum(pred), .groups = "drop")
  
  p <- ggplot(plot_data, aes(x = length)) +
    geom_col(aes(y = obs, fill = "Observed"), alpha = 0.7, width = 2) +
    geom_line(aes(y = pred, color = Scenario), linewidth = 1) +
    facet_wrap(~year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(title = paste(fishery_name, "- Length Frequency Fits"),
         x = "Length (cm)", y = "Frequency") +
    theme_bw() +
    theme(legend.position = "top", legend.box = "vertical",
          strip.text = element_text(size = 8))
  
  print(p)
  cat("\n\n")
}
```

## By scenario {.tabset .tabset-pills}

```{r lf-by-scenario, echo=FALSE, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis', eval=RUN_CHUNKS$lf_by_scenario}
# =============================================================================
# LENGTH FREQUENCY FITS BY SCENARIO
# =============================================================================

all_fisheries <- unique(unlist(lapply(LengOut_list, function(x) unique(x@lenfits$fishery))))
all_scenarios <- names(LengOut_list)

for (scenario_name in all_scenarios) {
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- LengOut_list[[scenario_name]]
  
  for (fish in all_fisheries) {
    fishery_name <- get_fishery_name(fish)
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    if (!(fish %in% unique(scenario_data@lenfits$fishery))) {
      cat("*No data available for this fishery in this scenario*\n\n")
      next
    }
    
    plot_data <- scenario_data@lenfits %>%
      filter(fishery == fish) %>%
      group_by(fishery, year, length) %>%
      summarise(obs = sum(obs), pred = sum(pred), .groups = "drop")
    
    if (nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    p <- ggplot(plot_data, aes(x = length)) +
      geom_col(aes(y = obs, fill = "Observed"), alpha = 0.7, width = 2) +
      geom_line(aes(y = pred, color = "Predicted"), linewidth = 1) +
      facet_wrap(~year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(title = paste(scenario_name, "-", fishery_name, "- Length Frequency Fits"),
           x = "Length (cm)", y = "Frequency") +
      theme_bw() +
      theme(legend.position = "top", legend.box = "horizontal",
            strip.text = element_text(size = 8))
    
    print(p)
    cat("\n\n")
  }
}
```


# WF plots {.tabset}

## Overlay all scenarios {.tabset .tabset-pills}

```{r wf-overlay, echo=FALSE, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis', eval=RUN_CHUNKS$wf_overlay}
# =============================================================================
# WEIGHT FREQUENCY FITS - ALL SCENARIOS OVERLAID
# =============================================================================

all_fisheries <- unique(unlist(lapply(WeightOut_list, function(x) unique(x@wgtfits$fishery))))

for (fish in all_fisheries) {
  fishery_name <- get_fishery_name(fish)
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  combined_data <- map_dfr(names(WeightOut_list), function(sc) {
    df <- WeightOut_list[[sc]]@wgtfits
    if (fish %in% unique(df$fishery)) {
      df %>% filter(fishery == fish) %>% mutate(Scenario = sc)
    } else {
      NULL
    }
  })
  
  if (nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, weight) %>%
    summarise(obs = sum(obs), pred = sum(pred), .groups = "drop")
  
  p <- ggplot(plot_data, aes(x = weight)) +
    geom_col(aes(y = obs, fill = "Observed"), alpha = 0.7, width = 2) +
    geom_line(aes(y = pred, color = Scenario), linewidth = 1) +
    facet_wrap(~year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(title = paste(fishery_name, "- Weight Frequency Fits"),
         x = "Weight (kg)", y = "Frequency") +
    theme_bw() +
    theme(legend.position = "top", legend.box = "vertical",
          strip.text = element_text(size = 8))
  
  print(p)
  cat("\n\n")
}
```

## By scenario {.tabset .tabset-pills}

```{r wf-by-scenario, echo=FALSE, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis', eval=RUN_CHUNKS$wf_by_scenario}
# =============================================================================
# WEIGHT FREQUENCY FITS BY SCENARIO
# =============================================================================

all_fisheries <- unique(unlist(lapply(WeightOut_list, function(x) unique(x@wgtfits$fishery))))
all_scenarios <- names(WeightOut_list)

for (scenario_name in all_scenarios) {
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- WeightOut_list[[scenario_name]]
  
  for (fish in all_fisheries) {
    fishery_name <- get_fishery_name(fish)
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    if (!(fish %in% unique(scenario_data@wgtfits$fishery))) {
      cat("*No data available for this fishery in this scenario*\n\n")
      next
    }
    
    plot_data <- scenario_data@wgtfits %>%
      filter(fishery == fish) %>%
      group_by(fishery, year, weight) %>%
      summarise(obs = sum(obs), pred = sum(pred), .groups = "drop")
    
    if (nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    p <- ggplot(plot_data, aes(x = weight)) +
      geom_col(aes(y = obs, fill = "Observed"), alpha = 0.7, width = 2) +
      geom_line(aes(y = pred, color = "Predicted"), linewidth = 1) +
      facet_wrap(~year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(title = paste(scenario_name, "-", fishery_name, "- Weight Frequency Fits"),
           x = "Weight (kg)", y = "Frequency") +
      theme_bw() +
      theme(legend.position = "top", legend.box = "horizontal",
            strip.text = element_text(size = 8))
    
    print(p)
    cat("\n\n")
  }
}
```
