---
title: "MFCL outputs"
author: "kyuhan Kim"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: yes
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      dpi = 160,
                      echo = F,
                      cache = F,
                      warning = F,
                      message = F, 
                      fig.path='../report/Figures/'
                      )

library(ggplot2)
library(cowplot)
library(dplyr)
library(FLR4MFCL)
library(tidyr)
library(patchwork)
library(reshape2)
library(kableExtra)
library(viridis)
library(stringr)


theme_set(theme_cowplot())


#########################
## load data and tools ##
#########################

source("../tools/plot_utils.R")

results <- list.dirs(file.path(getwd(), "..", "model"), full.names = TRUE, recursive = FALSE) %>%
  purrr::map(function(folder) {
    outputs_path <- normalizePath(folder, winslash = "/", mustWork = FALSE)
    cat("Processing folder:", outputs_path, "\n")
    
    # Read ParOut and RepOut for the current folder
    
    IndepOut <- if (file.exists(paste0(outputs_path, "/indepvar.rpt"))) {
      readLines(paste0(outputs_path, "/indepvar.rpt"))
    } else {
      NULL
    }
    
    ParOut <- read.MFCLPar(finalPar(outputs_path))
    RepOut <- read.MFCLRep(finalRep(outputs_path))
    LengOut <- read.MFCLLenFit(paste0(outputs_path, "/length.fit"))
    WeightOut <- read.MFCLWgtFit(paste0(outputs_path, "/weight.fit"))
    
    info <-readRDS(file.path(outputs_path, "info.rds"))
    
    output_files <- list.files(outputs_path, pattern = "^test_plot_output_\\d+$", full.names = TRUE)
    
    # Read each output file
    LikOut_list <- purrr::map(output_files, read.MFCLLikelihood)
    LikRawOut_list <- purrr::map(output_files, readLines)
    
        
    # Extract number only (e.g., '50' from 'test_plot_output_50')
    scales<-output_files %>% basename() %>% stringr::str_extract("\\d+$")
    
    names(LikRawOut_list) <- scales
    names(LikOut_list) <- scales
    
    # Return a list containing ParOut and RepOut
    list(ParOut = ParOut, 
         RepOut = RepOut, 
         LengOut = LengOut,
         WeightOut = WeightOut,
         LikOut=LikOut_list, 
         LikRawOut=LikRawOut_list,
         scales=scales,
         IndepOut=IndepOut,
         info=info)
  })


# Convert results into a named list, using folder names as keys
names(results) <- basename(list.dirs(file.path(getwd(), "..", "model"), full.names = TRUE, recursive = FALSE))

# Access individual ParOut and RepOut
ParOut_list <- purrr::map(results, "ParOut")
RepOut_list <- purrr::map(results, "RepOut")
WeightOut_list <- purrr::map(results, "WeightOut")
LengOut_list <- purrr::map(results, "LengOut")
IndepOut_list <- purrr::map(results, "IndepOut")

Info_list <- purrr::map(results, "info")


# Access individual LikOut objects
ProfLikOut_list <- purrr::map(results, "LikOut")
ProfLikOutRaw_list <- purrr::map(results, "LikRawOut")


minYear=1952
maxYear=2021

# opacity and line width
alpha = 0.5
linewidth = 1
# 
# scenario_colors <- c(
#   "base" = "#1b9e77",
#   "m1" = "#d95f02",
#   "m2" = "#e6ab02"
# )
# 
# # Fisheries mapping (option for renaming fisheries)

all_fisheries_mapping <- c(
  "1" = "LL-ALL-1",
  "2" = "LL-ALL-2",
  "3" = "LL-US-2",
  "4" = "LL-ALL-3",
  "5" = "LL-OS-3",
  "6" = "LL-OS-7",
  "7" = "LL-ALL-7",
  "8" = "LL-ALL-8",
  "9" = "LL-ALL-4",
  "10" = "LL-AU-5",
  "11" = "LL-ALL-5",
  "12" = "LL-ALL-6",
  "13" = "PS-ASS-3",
  "14" = "PS-UNA-3",
  "15" = "PS-ASS-4",
  "16" = "PS-UNA-4",
  "17" = "MISC-PH-7",
  "18" = "HL-PHID-7",
  "19" = "PS-JP-1",
  "20" = "PL-JP-1",
  "21" = "PL-ALL-3",
  "22" = "PL-ALL-8",
  "23" = "MISC-ID-7",
  "24" = "PS-PHID-7",
  "25" = "PS-ASS-8",
  "26" = "PS-UNA-8",
  "27" = "LL-AU-9",
  "28" = "PL-ALL-7",
  "29" = "LL-ALL-9",
  "30" = "PS-ASS-7",
  "31" = "PS-UNA-7",
  "32" = "MISC-VN-7",
    "33" = "LL-ALL-1i",
    "34" = "LL-ALL-2i",
    "35" = "LL-ALL-3i",
    "36" = "LL-ALL-4i",
    "37" = "LL-ALL-5i",
    "38" = "LL-ALL-6i",
    "39" = "LL-ALL-7i",
    "40" = "LL-ALL-8i",
    "41" = "LL-ALL-9i"
)


index_fisheries_mapping <- c(
  "33" = "LL-ALL-1",
  "34" = "LL-ALL-2",
  "35" = "LL-ALL-3",
  "36" = "LL-ALL-4",
  "37" = "LL-ALL-5",
  "38" = "LL-ALL-6",
  "39" = "LL-ALL-7",
  "40" = "LL-ALL-8",
  "41" = "LL-ALL-9"
)

# 
# # Filtered fisheries
 fisheries <- names(index_fisheries_mapping)

model_names <- names(ParOut_list)

```


# Summary of each model configuration

```{r, echo=FALSE, message=F, fig.dim=c(10,10)}
# Extract parameters (max_grad, obj_fun, n_pars, dimensions) from ParOut_list
ExtractParams <- lapply(seq_along(ParOut_list), function(i) {
  model_name <- names(ParOut_list)[i]  # Get the scenario name
  
  mgc_value <- tryCatch(
    ParOut_list[[i]]@max_grad,
    error = function(e) NA  # If an error occurs, return NA
  )
  
  obj_fun_value <- tryCatch(
    ParOut_list[[i]]@obj_fun,
    error = function(e) NA  # If an error occurs, return NA
  )
  
  n_pars_value <- tryCatch(
    ParOut_list[[i]]@n_pars,
    error = function(e) NA  # If an error occurs, return NA
  )
  
  dimensions_value <- tryCatch(
    as.list(ParOut_list[[i]]@dimensions),
    error = function(e) list(agecls = NA, years = NA, seasons = NA, regions = NA, fisheries = NA, taggrps = NA)  # Default NA if error
  )
  
  data.frame(Model = model_name, mgc = mgc_value, obj_fun = obj_fun_value, n_pars = n_pars_value, 
             agecls = dimensions_value$agecls, years = dimensions_value$years, 
             seasons = dimensions_value$seasons, regions = dimensions_value$regions, 
             fisheries = dimensions_value$fisheries, taggrps = dimensions_value$taggrps)
})

# Combine results into a single data frame
params_df <- bind_rows(ExtractParams)

# Clean scenario names, round numeric values, and apply scenario order
params_df <- params_df %>%
  mutate(
    mgc      = ifelse(!is.na(as.numeric(mgc)), round(as.numeric(mgc), 6), NA),
    obj_fun  = ifelse(!is.na(as.numeric(obj_fun)), round(as.numeric(obj_fun), 2), NA),
    n_pars   = ifelse(!is.na(as.numeric(n_pars)), as.numeric(n_pars), NA)  # Ensure n_pars is numeric
  ) 

# Display parameter values table with scenario-specific dimensions
kable(params_df, caption = "Basic model info") %>%
  kable_styling(full_width = FALSE)

```




# Bound Hit Parameter Analysis {.tabset .tabset-pills}

```{r bound-hit-analysis, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Parse function
parse_indepvar <- function(lines) {
  data_list <- list()
  for (i in 2:length(lines)) {
    line <- lines[i]
    if (nchar(trimws(line)) > 0) {
      hit_bound <- grepl("\\*{5,}", line)
      line_clean <- gsub("\\*+", "", line)
      parts <- strsplit(trimws(line_clean), "\\s+")[[1]]
      
      if (length(parts) >= 6) {
        data_list[[length(data_list) + 1]] <- data.frame(
          Index = as.integer(parts[1]),
          Var_name = parts[2],
          Estimate = as.numeric(parts[3]),
          L_bound = as.numeric(parts[4]),
          U_bound = as.numeric(parts[5]),
          Gradient = as.numeric(parts[6]),
          Hit_Bound = hit_bound,
          stringsAsFactors = FALSE
        )
      }
    }
  }
  do.call(rbind, data_list)
}

# Separate NULL and valid models
null_models <- names(IndepOut_list)[sapply(IndepOut_list, is.null)]
valid_models <- names(IndepOut_list)[!sapply(IndepOut_list, is.null)]

# Process each valid model
model_results <- list()

for (model_name in valid_models) {
  lines <- IndepOut_list[[model_name]]
  df <- parse_indepvar(lines)
  
  df$Distance_to_lower <- abs(df$Estimate - df$L_bound)
  df$Distance_to_upper <- abs(df$Estimate - df$U_bound)
  df$Hit_Type <- ifelse(!df$Hit_Bound, "None",
                        ifelse(df$Distance_to_lower <= df$Distance_to_upper, "Lower", "Upper"))
  df$Distance_to_bound <- ifelse(!df$Hit_Bound, NA,
                                 ifelse(df$Hit_Type == "Lower", df$Distance_to_lower, df$Distance_to_upper))
  df$Var_type <- str_extract(df$Var_name, "^[a-zA-Z_]+")
  
  bound_hits <- df %>%
    filter(Hit_Bound) %>%
    select(Index, Var_name, Var_type, Estimate, Hit_Type, 
           L_bound, U_bound, Distance_to_bound, Gradient) %>%
    arrange(Index)
  
  model_results[[model_name]] <- list(
    total_params = nrow(df),
    bound_hits = bound_hits
  )
  
  write.csv(bound_hits, paste0("bound_hits_", model_name, ".csv"), row.names = FALSE)
}

# Overview Tab
cat("\n## Overview\n\n")

cat(sprintf("**Total Models:** %d  \n", length(IndepOut_list)))
cat(sprintf("**Models with indepvar.rpt:** %d  \n", length(valid_models)))
cat(sprintf("**Models without indepvar.rpt:** %d  \n\n", length(null_models)))

if (length(model_results) > 0) {
  overview <- data.frame(
    Model = names(model_results),
    Total_Params = sapply(model_results, function(x) x$total_params),
    Bound_Hits = sapply(model_results, function(x) nrow(x$bound_hits)),
    Hit_Rate = sapply(model_results, function(x) 
      sprintf("%.2f%%", nrow(x$bound_hits) / x$total_params * 100)),
    Lower_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Lower")),
    Upper_Hits = sapply(model_results, function(x) 
      sum(x$bound_hits$Hit_Type == "Upper"))
  )
  
 print(
    kable(overview,
          col.names = c("Model", "Total", "Hits", "Rate", "Lower", "Upper"),
          align = c("l", "r", "r", "r", "r", "r"),
          row.names = FALSE) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE) %>%
      row_spec(0, bold = TRUE, background = "#2196F3", color = "white") %>%
      column_spec(3, bold = TRUE, color = "red")
  )
}

if (length(null_models) > 0) {
  cat("\n\n### Models Without indepvar.rpt\n\n")
  cat("The following models did not generate an `indepvar.rpt` file:\n\n")
  for (model in null_models) {
    cat(sprintf("- **%s**: `indepvar.rpt` was not generated\n", model))
  }
  cat("\n")
}

# Valid Model Tabs
for (model_name in names(model_results)) {
  result <- model_results[[model_name]]
  bound_hits <- result$bound_hits
  
  cat(sprintf("\n## %s\n\n", model_name))
  
  cat(sprintf("**Total Parameters:** %s  \n", format(result$total_params, big.mark = ",")))
  cat(sprintf("**Bound Hits:** %d (%.2f%%)  \n", 
              nrow(bound_hits), 
              nrow(bound_hits) / result$total_params * 100))
  cat(sprintf("**Lower Bound Hits:** %d  \n", sum(bound_hits$Hit_Type == "Lower")))
  cat(sprintf("**Upper Bound Hits:** %d  \n\n", sum(bound_hits$Hit_Type == "Upper")))
  
  if (nrow(bound_hits) > 0) {
    
    cat("### Bound Hit Parameters\n\n")
    
    bound_hits_display <- bound_hits %>%
      mutate(
        Estimate_fmt = sprintf("%.4e", Estimate),
        Distance_fmt = sprintf("%.2e", Distance_to_bound)
      ) %>%
      select(Index, Var_name, Var_type, Estimate_fmt, Hit_Type, L_bound, U_bound, Distance_fmt)
    
    print(
      kable(bound_hits_display, 
            col.names = c("Index", "Parameter", "Type", "Estimate", "Hit", 
                          "Lower", "Upper", "Distance"),
            align = c("r", "l", "l", "r", "c", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                      full_width = TRUE,
                      font_size = 11) %>%
        row_spec(0, bold = TRUE, background = "#4CAF50", color = "white") %>%
        column_spec(5, bold = TRUE, 
                    color = ifelse(bound_hits$Hit_Type == "Lower", "#E74C3C", "#3498DB")) %>%
        scroll_box(width = "100%", height = "400px")
    )
    
    cat("\n\n### Summary by Variable Type\n\n")
    
    type_summary <- bound_hits %>%
      count(Var_type, Hit_Type) %>%
      pivot_wider(names_from = Hit_Type, values_from = n, values_fill = 0) %>%
      mutate(Total = Lower + Upper) %>%
      arrange(desc(Total))
    
    print(
      kable(type_summary,
            col.names = c("Type", "Lower", "Upper", "Total"),
            align = c("l", "r", "r", "r")) %>%
        kable_styling(bootstrap_options = c("striped", "hover"),
                      full_width = FALSE) %>%
        row_spec(0, bold = TRUE, background = "#FF9800", color = "white") %>%
        column_spec(4, bold = TRUE)
    )
    
    cat(sprintf("\n\n*Data saved to: `bound_hits_%s.csv`*\n\n", model_name))
    
  } else {
    cat("\n✅ **No bound hits detected in this model**\n\n")
  }
}

# NULL Model Tabs
for (model_name in null_models) {
  cat(sprintf("\n## %s\n\n", model_name))
  cat("⚠️ **No`indepvar.rpt` file.**\n\n")
}


```



# Spawning depletion

```{r Dep, echo=FALSE, message=F, fig.dim=c(8,6)}

SBdep <- GetQuantSimple(SBSBF0, RepOut_list, minYear, maxYear)
Rec <- GetQuantSimple(eq_rec, RepOut_list, minYear, maxYear, scale_factor = 1/1e6)

## Define colour palette
scenario_levels <- unique(SBdep$Scenario)
n_colors <- length(scenario_levels)
scenario_colors <- setNames(
  viridis(n_colors, option = "D", direction = 1),
  scenario_levels
)

# Convert to factor
SBdep$Scenario <- factor(SBdep$Scenario, levels = scenario_levels)
Rec$Scenario <- factor(Rec$Scenario, levels = scenario_levels)

## Plot 1: SB/SBF=0
SBdepPlot <- ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) + 
  geom_line(linewidth = 1.2) + 
  scale_color_manual(values = scenario_colors) + 
  labs(x = "Year", y = bquote(SB/SB["F=0"])) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "darkred") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgreen") +
  theme_bw() +
  theme(legend.position = "none")

## Plot 2: Recruitment
RecPlot <- ggplot(Rec, aes(x = Year, y = Quant, color = Scenario, group = Scenario)) + 
  geom_line(linewidth = 1.2) + 
  coord_cartesian(ylim = c(0, NA)) +
  scale_color_manual(values = scenario_colors) + 
  labs(x = "Year", y = bquote("Spawning Potential (" * 10^3 * " MT)")) +
  theme_bw() +
  theme(legend.position = "none")

# Extract legend
temp_plot <- ggplot(SBdep, aes(x = Year, y = Quant, color = Scenario)) +
  geom_line(linewidth = 2) +
  scale_color_manual(values = scenario_colors) +
  theme_bw() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    legend.key.width = unit(1.5, "cm")
  ) +
  labs(color = "Scenario")

legend <- cowplot::get_legend(temp_plot)

combined_plot <- cowplot::plot_grid(
  SBdepPlot, RecPlot,
  ncol = 1,
  labels = c("A", "B"),
  label_size = 12,
  align = "v"
)

final_plot <- cowplot::plot_grid(
  combined_plot, legend,
  ncol = 2,
  rel_widths = c(4, 1)
)

print(final_plot)
```


# Likelihood profile {.tabset}

## Each component

```{r model_profile, echo=FALSE, message=F, fig.dim=c(8,8)}

run_prof_all <- sapply(Info_list, function(x) x$run_prof)

PenIndex="do_everything"
pen_idx <- grep("do_everything", ProfLikOutRaw_list)

## make sure the scenario names are in the same order as LikOut_list

scenarios_prof <- names(run_prof_all)[run_prof_all == 1]
scenarios_name <- intersect(names(ProfLikOut_list), scenarios_prof)

if(length(scenarios_name) >0) {
 

Likes=list()

for( j in 1:length(results)) {
  
  scales=results[[j]]$scales
  
  for (i in scales) {
    Likes[[as.character(i)]]=sapply(scenarios_name, function(x) c("Indices"=sum(ProfLikOut_list[[x]][[as.character(i)]]@survey_index),
                                                                            "LFs"=sum(ProfLikOut_list[[x]][[as.character(i)]]@total_length_fish),
                                                                             "Penalties"=as.numeric(ProfLikOutRaw_list[[x]][[as.character(i)]][pen_idx:(pen_idx + 1)][2]),
                                                                            "WFs"=sum(ProfLikOut_list[[x]][[as.character(i)]]@total_weight_fish),
                                                                            "Tags"=sum(unlist(ProfLikOut_list[[x]][[as.character(i)]]@tag_rel_fish, recursive = T)) ) )
    
    
    Likes[[i]]=rbind(Likes[[i]],  "Total"=apply(Likes[[i]], 2, sum)
    )
    
  }
  
}



Likes_df <- purrr::imap_dfr(Likes, function(df, indicator) {
  as.data.frame(df) %>%
    tibble::rownames_to_column("Likelihood") %>%
    mutate(scaler = indicator)
})

Likes_long <- Likes_df %>%
  pivot_longer(
    cols = scenarios_name,
    names_to = "scenario",
    values_to = "value"
  ) %>%
  mutate(scaler = as.numeric(scaler)*0.01*unlist(sapply(scenarios_name, function(x) read.table(paste0("../model/",x, "/avg_bio"))))
)


Likes_change <- Likes_long %>%
  group_by(Likelihood, scenario) %>%
  mutate(
    min_value = min(value, na.rm = TRUE),
    change = (value - min_value)
  ) %>%
  ungroup()

Likes_change %>% 
  #filter(Likelihood != "Penalties") %>%
  ggplot(aes(x = scaler, y = change, colour = Likelihood)) +
  geom_line(linewidth = 1, alpha=0.7) +
  #geom_point() +
  scale_color_viridis_d() +
  facet_wrap(~scenario, scale="free") +
  scale_x_continuous(
    labels = function(x) x / 1000,
    name=bquote("Average biomass ("*10^3*" MT)"),
  ) +
  labs(
    y = "Changes in Likelihood",
    colour = "Likelihood"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    strip.text = element_text(size = 10, face = "bold")
  )


}

```

## Piner (LFs)

```{r piner_LFs, echo=FALSE, message=F, fig.dim=c(8,8)}
run_prof_all <- sapply(Info_list, function(x) x$run_prof)

PenIndex="do_everything"
pen_idx <- grep("do_everything", ProfLikOutRaw_list)

scenarios_prof <- names(run_prof_all)[run_prof_all == 1]
scenarios_name <- intersect(names(ProfLikOut_list), scenarios_prof)

if(length(scenarios_name) > 0) {
  
  Likes = list()
  
  for(j in 1:length(results)) {
    
    scales = results[[j]]$scales
    
    for (i in scales) {
      
      # Extract all elements from total_length_fish for each scenario
      Likes[[as.character(i)]] = sapply(scenarios_name, function(x) {
        
        lf_vector = ProfLikOut_list[[x]][[as.character(i)]]@total_length_fish
        
        # Map to fishery names
        names(lf_vector) = all_fisheries_mapping[as.character(1:length(lf_vector))]
        
        return(lf_vector)
      })
      
      # Remove rows (components) that are 0 across all scenarios
      Likes[[i]] = Likes[[i]][rowSums(Likes[[i]] != 0) > 0, , drop = FALSE]
      
      # Add Total row
      Likes[[i]] = rbind(Likes[[i]], "Total" = apply(Likes[[i]], 2, sum))
    }
  }
  
  # Convert to dataframe
  Likes_df <- purrr::imap_dfr(Likes, function(df, indicator) {
    as.data.frame(df) %>%
      tibble::rownames_to_column("Fishery") %>%
      mutate(scaler = indicator)
  })
  
  # Convert to long format
  Likes_long <- Likes_df %>%
    pivot_longer(
      cols = scenarios_name,
      names_to = "scenario",
      values_to = "value"
    ) %>%
    mutate(scaler = as.numeric(scaler) * 0.01 * 
             unlist(sapply(scenarios_name, function(x) 
               read.table(paste0("../model/", x, "/avg_bio"))))
    )
  
  # Calculate change from minimum value
  Likes_change <- Likes_long %>%
    group_by(Fishery, scenario) %>%
    mutate(
      min_value = min(value, na.rm = TRUE),
      change = (value - min_value)
    ) %>%
    ungroup()
  
  # Visualization with LFs annotation in top-right corner
  Likes_change %>% 
    filter(Fishery != "Total") %>%
    ggplot(aes(x = scaler, y = change, colour = Fishery, shape = Fishery)) +
    geom_line(linewidth = 1, alpha = 0.7) +
    geom_point(size = 2, alpha = 0.8) +
    annotate("text", x = Inf, y = Inf, label = "LFs", 
             hjust = 1.1, vjust = 1.5, size = 5, fontface = "bold") +
    scale_color_viridis_d() +
    scale_shape_manual(values = rep(0:24, length.out = length(unique(Likes_change$Fishery)))) +
    facet_wrap(~scenario, scale = "free") +
    scale_x_continuous(
      labels = function(x) x / 1000,
      name = bquote("Average biomass ("*10^3*" MT)")
    ) +
    labs(
      y = "Changes in Likelihood",
      colour = "Fishery",
      shape = "Fishery"
    ) +
    theme(
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 10, face = "bold")
    )
}

```



## Piner (WFs)

```{r piner_WFs, echo=FALSE, message=F, fig.dim=c(8,8)}
run_prof_all <- sapply(Info_list, function(x) x$run_prof)

PenIndex="do_everything"
pen_idx <- grep("do_everything", ProfLikOutRaw_list)

scenarios_prof <- names(run_prof_all)[run_prof_all == 1]
scenarios_name <- intersect(names(ProfLikOut_list), scenarios_prof)

if(length(scenarios_name) > 0) {
  
  Likes = list()
  
  for(j in 1:length(results)) {
    
    scales = results[[j]]$scales
    
    for (i in scales) {
      
      # Extract all elements from total_weight_fish for each scenario
      Likes[[as.character(i)]] = sapply(scenarios_name, function(x) {
        
        wf_vector = ProfLikOut_list[[x]][[as.character(i)]]@total_weight_fish
        
        # Map to fishery names
        names(wf_vector) = all_fisheries_mapping[as.character(1:length(wf_vector))]
        
        return(wf_vector)
      })
      
      # Remove rows (components) that are 0 across all scenarios
      Likes[[i]] = Likes[[i]][rowSums(Likes[[i]] != 0) > 0, , drop = FALSE]
      
      # Add Total row
      Likes[[i]] = rbind(Likes[[i]], "Total" = apply(Likes[[i]], 2, sum))
    }
  }
  
  # Convert to dataframe
  Likes_df <- purrr::imap_dfr(Likes, function(df, indicator) {
    as.data.frame(df) %>%
      tibble::rownames_to_column("Fishery") %>%
      mutate(scaler = indicator)
  })
  
  # Convert to long format
  Likes_long <- Likes_df %>%
    pivot_longer(
      cols = scenarios_name,
      names_to = "scenario",
      values_to = "value"
    ) %>%
    mutate(scaler = as.numeric(scaler) * 0.01 * 
             unlist(sapply(scenarios_name, function(x) 
               read.table(paste0("../model/", x, "/avg_bio"))))
    )
  
  # Calculate change from minimum value
  Likes_change <- Likes_long %>%
    group_by(Fishery, scenario) %>%
    mutate(
      min_value = min(value, na.rm = TRUE),
      change = (value - min_value)
    ) %>%
    ungroup()
  
  # Visualization with WFs annotation in top-right corner
  Likes_change %>% 
    filter(Fishery != "Total") %>%
    ggplot(aes(x = scaler, y = change, colour = Fishery, shape = Fishery)) +
    geom_line(linewidth = 1, alpha = 0.7) +
    geom_point(size = 2, alpha = 0.8) +
    annotate("text", x = Inf, y = Inf, label = "WFs", 
             hjust = 1.1, vjust = 1.5, size = 5, fontface = "bold") +
    scale_color_viridis_d() +
    scale_shape_manual(values = rep(0:24, length.out = length(unique(Likes_change$Fishery)))) +
    facet_wrap(~scenario, scale = "free") +
    scale_x_continuous(
      labels = function(x) x / 1000,
      name = bquote("Average biomass ("*10^3*" MT)")
    ) +
    labs(
      y = "Changes in Likelihood",
      colour = "Fishery",
      shape = "Fishery"
    ) +
    theme(
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 10, face = "bold")
    )
}

```


# CPUE plots  {.tabset}

## Observed vs Fitted CPUE by scenario {.tabset .tabset-pills}

```{r cpue-plots-by-scenario, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.dim=c(8,8)}
# Global configuration for easy tweaks
config <- list(
  alpha = 0.7,
  linewidth = 1,
  point_size = 1.5,
  observed_color = "grey30",
  predicted_colors = "coral",
  legend_position = "bottom",
  facet_ncol = 3
)

# Create plots
scenario_plots <- create_cpue_plots(
  RepOut_list = RepOut_list,
  fisheries = fisheries,
  fisheries_mapping = index_fisheries_mapping,
  viridis_option = "viridis"
)

# Print each scenario in its own tab
for (nm in names(scenario_plots)) {
  cat(sprintf("\n### %s\n\n", nm))
  print(scenario_plots[[nm]])
  cat("\n\n")
}
```


## overlay all scenarios in one plot (Interactive)

```{r, echo=FALSE, message=FALSE, fig.dim=c(10,8), eval=F}
library(plotly)

overlay_plot <- create_overlay_cpue_plot(
  RepOut_list = RepOut_list,
  fisheries = fisheries,
  fisheries_mapping = index_fisheries_mapping,
  viridis_option = "viridis",
  custom_config = list(predicted_colors=NULL)
)

# Convert to interactive plotly
interactive_plot <- ggplotly(overlay_plot, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(
      orientation = "v",
      x = 1.02,
      y = 1,
      xanchor = "left",
      yanchor = "top"
    )
  )

interactive_plot
```

# LF plots  {.tabset}

## overlay all scenarios in one plot {.tabset .tabset-pills}

```{r lf-plots-setup1, eval=F, echo=FALSE, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis'}
# Get all unique fisheries across all scenarios
all_fisheries <- unique(unlist(lapply(LengOut_list, function(x) unique(x@lenfits$fishery))))

# Loop through each fishery
for(fish in all_fisheries) {
  
  # Map fishery number to name
  fishery_name <- all_fisheries_mapping[as.character(fish)]
  if(is.na(fishery_name)) fishery_name <- paste("Fishery", fish)
  
  # Create tab for this fishery
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  # Combine data from all scenarios for this fishery
  combined_data <- lapply(names(LengOut_list), function(scenario_name) {
    
    scenario_data <- LengOut_list[[scenario_name]]
    
    if(fish %in% unique(scenario_data@lenfits$fishery)) {
      scenario_data@lenfits %>%
        filter(fishery == fish) %>%
        mutate(Scenario = scenario_name)
    } else {
      NULL
    }
  }) %>%
    bind_rows()
  
  # Skip if no data for this fishery
  if(nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  # Aggregate by scenario, year, and length
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, length) %>%
    summarise(obs = sum(obs), 
              pred = sum(pred),
              .groups = "drop")
  
  # Create plot
  p <- ggplot(plot_data, aes(x = length)) +
    geom_col(aes(y = obs, fill = "Observed"), 
             alpha = 0.7, width = 2) +
    geom_line(aes(y = pred, color = Scenario), 
              linewidth = 1) +
    facet_wrap(~ year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(title = paste(fishery_name, "- Length Frequency Fits"),
         x = "Length (cm)", 
         y = "Frequency") +
    theme_bw() +
    theme(
      legend.position = "top",
      legend.box = "vertical",
      strip.text = element_text(size = 8)
    )
  
  print(p)
  cat("\n\n")
}
```


## Observed vs Fitted LFs by scenario {.tabset .tabset-pills}

```{r lf-plots-setup, echo=FALSE, eval=F, message=FALSE, fig.dim=c(8,10), warning=FALSE, results='asis'}
# Get all unique fisheries across all scenarios
all_fisheries <- unique(unlist(lapply(LengOut_list, function(x) unique(x@lenfits$fishery))))

# Get all scenarios
all_scenarios <- names(LengOut_list)

# Loop through each scenario first
for(scenario_name in all_scenarios) {
  
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- LengOut_list[[scenario_name]]
  
  # Loop through each fishery within this scenario
  for(fish in all_fisheries) {
    
    # Map fishery number to name
    fishery_name <- all_fisheries_mapping[as.character(fish)]
    if(is.na(fishery_name)) fishery_name <- paste("Fishery", fish)
    
    # Create sub-tab for this fishery
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    # Get data for this fishery in this scenario
    if(!(fish %in% unique(scenario_data@lenfits$fishery))) {
      cat("*No data available for this fishery in this scenario*\n\n")
      next
    }
    
    plot_data <- scenario_data@lenfits %>%
      filter(fishery == fish)
    
    if(nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    # Aggregate by year and length
    plot_data <- plot_data %>%
      group_by(fishery, year, length) %>%
      summarise(obs = sum(obs), 
                pred = sum(pred),
                .groups = "drop")
    
    # Create plot
    p <- ggplot(plot_data, aes(x = length)) +
      geom_col(aes(y = obs, fill = "Observed"), 
               alpha = 0.7, width = 2) +
      geom_line(aes(y = pred, color = "Predicted"), 
                linewidth = 1) +
      facet_wrap(~ year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(title = paste(scenario_name, "-", fishery_name, "- Length Frequency Fits"),
           x = "Length (cm)", 
           y = "Frequency") +
      theme_bw() +
      theme(
        legend.position = "top",
        legend.box = "horizontal",
        strip.text = element_text(size = 8)
      )
    
    print(p)
    cat("\n\n")
  }
}
```




# WF plots  {.tabset}


## overlay all scenarios in one plot {.tabset .tabset-pills}

```{r wf-plots-setup1, echo=FALSE, eval=F, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis'}
# Get all unique fisheries across all scenarios
all_fisheries <- unique(unlist(lapply(WeightOut_list, function(x) unique(x@wgtfits$fishery))))

# Loop through each fishery
for(fish in all_fisheries) {
  
  # Map fishery number to name
  fishery_name <- all_fisheries_mapping[as.character(fish)]
  if(is.na(fishery_name)) fishery_name <- paste("Fishery", fish)
  
  # Create tab for this fishery
  cat(sprintf("\n### %s\n\n", fishery_name))
  
  # Combine data from all scenarios for this fishery
  combined_data <- lapply(names(WeightOut_list), function(scenario_name) {
    
    scenario_data <- WeightOut_list[[scenario_name]]
    
    if(fish %in% unique(scenario_data@wgtfits$fishery)) {
      scenario_data@wgtfits %>%
        filter(fishery == fish) %>%
        mutate(Scenario = scenario_name)
    } else {
      NULL
    }
  }) %>%
    bind_rows()
  
  # Skip if no data for this fishery
  if(nrow(combined_data) == 0) {
    cat("*No data available for this fishery*\n\n")
    next
  }
  
  # Aggregate by scenario, year, and weight
  plot_data <- combined_data %>%
    group_by(Scenario, fishery, year, weight) %>%
    summarise(obs = sum(obs), 
              pred = sum(pred),
              .groups = "drop")
  
  # Create plot
  p <- ggplot(plot_data, aes(x = weight)) +
    geom_col(aes(y = obs, fill = "Observed"), 
             alpha = 0.7, width = 2) +
    geom_line(aes(y = pred, color = Scenario), 
              linewidth = 1) +
    facet_wrap(~ year, scales = "free_y", ncol = 4) +
    scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
    scale_color_viridis_d(name = "Scenario") +
    labs(title = paste(fishery_name, "- Weight Frequency Fits"),
         x = "Weight (kg)", 
         y = "Frequency") +
    theme_bw() +
    theme(
      legend.position = "top",
      legend.box = "vertical",
      strip.text = element_text(size = 8)
    )
  
  print(p)
  cat("\n\n")
}
```



## Observed vs Fitted WFs by scenario {.tabset .tabset-pills}

```{r wf-plots-setup, echo=FALSE, eval=F, message=FALSE, fig.dim=c(8,12), warning=FALSE, results='asis'}
# Get all unique fisheries across all scenarios
all_fisheries <- unique(unlist(lapply(WeightOut_list, function(x) unique(x@wgtfits$fishery))))

# Get all scenarios
all_scenarios <- names(WeightOut_list)

# Loop through each scenario first
for(scenario_name in all_scenarios) {
  
  cat(sprintf("\n### %s {.tabset}\n\n", scenario_name))
  
  scenario_data <- WeightOut_list[[scenario_name]]
  
  # Loop through each fishery within this scenario
  for(fish in all_fisheries) {
    
    # Map fishery number to name
    fishery_name <- all_fisheries_mapping[as.character(fish)]
    if(is.na(fishery_name)) fishery_name <- paste("Fishery", fish)
    
    # Create sub-tab for this fishery
    cat(sprintf("\n#### %s\n\n", fishery_name))
    
    # Get data for this fishery in this scenario
    if(!(fish %in% unique(scenario_data@wgtfits$fishery))) {
      cat("*No data available for this fishery in this scenario*\n\n")
      next
    }
    
    plot_data <- scenario_data@wgtfits %>%
      filter(fishery == fish)
    
    if(nrow(plot_data) == 0) {
      cat("*No data available for this fishery*\n\n")
      next
    }
    
    # Aggregate by year and weight
    plot_data <- plot_data %>%
      group_by(fishery, year, weight) %>%
      summarise(obs = sum(obs), 
                pred = sum(pred),
                .groups = "drop")
    
    # Create plot
    p <- ggplot(plot_data, aes(x = weight)) +
      geom_col(aes(y = obs, fill = "Observed"), 
               alpha = 0.7, width = 2) +
      geom_line(aes(y = pred, color = "Predicted"), 
                linewidth = 1) +
      facet_wrap(~ year, scales = "free_y", ncol = 4) +
      scale_fill_manual(name = "", values = c("Observed" = "#E69F00")) +
      scale_color_manual(name = "", values = c("Predicted" = "#56B4E9")) +
      labs(title = paste(scenario_name, "-", fishery_name, "- Weight Frequency Fits"),
           x = "Weight (kg)", 
           y = "Frequency") +
      theme_bw() +
      theme(
        legend.position = "top",
        legend.box = "horizontal",
        strip.text = element_text(size = 8)
      )
    
    print(p)
    cat("\n\n")
  }
}
```
